### 2016-01-31 Tex/paper.tex
partial differential equation

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{booktabs}
\usepackage{caption2}
\usepackage{epstopdf}
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}                     %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\renewcommand{\captionlabelfont}{\small \bfseries \rmfamily}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

\begin{document}

\title{Human Capital Model} \date{\today{}}
\maketitle

\tableofcontents

\newpage

\section{Introduction}
\label{sec:introduction}

Considering the shortage of the talent, it's essential for companys to
retain good people and make them well-trained. However, current
situation is not satisfactory while many talents always tend to get a
good job via job-hopping, causing orgnizational churn in employees who
are closely connected to them. In order to simulate this process and
improve it, we build a human capital model based on Social Network
Analysis and Markov process. 456

\subsection{Restatement of the Problem}
\label{sec:restatement-of-the-problem}

\subsection{Literature Review}
\label{sec:literature-review}

\begin{itemize}
\item
\item
\item
\end{itemize}

\section{Terminology}
\label{sec:terminology}

\begin{itemize}
\item
\item
\item
\end{itemize}

\section{Assumptions and Justifications}
\label{sec:assumptions-and-justifications}

\begin{itemize}
\item \textbf{assumption 1} If an employee has probability to
  promote, he won't churn.

The possibility of the unforeseen accidents, which could force an
employee to leave his position,is neglected.Human nature, an employee
will stay at his position to chase for higher level.

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already,ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5,it is wasteful to recruit for a
position if an employee can promote to it.

\item \textbf{assumption 3} Demotion won't occur.

\item \textbf{assumption 4} Administrative clerk won't promote or be
  transferred.

\item \textbf{assumption 5} For the promotion probability and
  organization change, the other factors effects the churn probability
  is invariable.

Though churn derives from varieties of reasons and they are actually
lacking of known conditions and data to estimate them, we have to
regard it as stable in our model.

\item \textbf{assumption 6} Each division or office have at least one
  middle manager or senior manager.

\end{itemize}

% the main section of the paper
\section{Human Capital Model}
\label{sec:human-capital-model}

\subsection{Model Overview}
\label{sec:model-overview}

Partial differential equations are widely used in natural science, engineering and economical management.
It is natural to use partial differential equation to solve this physical problem.

Definitions of symbols employed in this paper are listed in
\textbf{Table 1}.
\begin{table}
\begin{tabular}{|l|l|}
  Variable & Description \\
  \hline
  $i$            &Index of an employee \\
  $L_{i,t}$          &The level of $i$ \\
  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
  $a_{ij,t}$        &Represent the influence caused by relationship
                    between superior and subordinate \\
  $f_{ij,t}$        &Represent the influence caused by relationship
                    between person with many friends and person with
                    few friends \\
  $c_{i,t}$        &Clustering Coefficient of $i$
\end{tabular}
\end{table}

\subsection{Human Performance Model}
\label{sec:human-model}

In this part, we buid a people model to evaluate an employee in four
aspects, in terms of \textbf{Quantitative Management Performance} ---
work achievement, work ability, work attitude and potential. These
four aspects are supposed to be quantized according to annual
evaluation based on performance as judged by the supervisor and we
take these independent variables as $A_{ac_i}$, $A_{ab_1}$, $A_{at_i}$
and $A_{po_i}$ for each employee $i$. For each of the four parameters,
it goes from 0 to 1. The statues are used for calculating the
probability that employee can promote. Meanwhile, they influence
leaving probability and team cohesiveness as well.

It is obvious that some of the parameters are somehow more important
than others. So in an effort to make our model more accurate and
reliable,we introduce a weighted index of deviation $AD_i$, with
\begin{equation}
  A_i=w_{ac} \cdot A_{ac_i} + w_{ab} \cdot A_{ab_i} + w_{at} \cdot A_{at_i} +
  w_{po} \cdot A_{po_i}
\end{equation}

We determine weights via the Analytical Hierarchy Process(AHP) [Saaty
1982]. We build a $4 \times 4$ reciprocal matrix by pair comparison:
\begin{center}
\begin{tabular}{|c|c|c|c|c|}
\hline
       &$A_{ac}$      &$A_{ab}$  &$A_{at}$    &$A_{po}$  \\ \hline
 $A_{ac}$ & 1           & 5 & 2            &1            \\ \hline
 $A_{ab}$ &$\frac{1}{5}$ & 1 &$\frac{1}{3}$ & $\frac{1}{4}$\\ \hline
 $A_{at}$ &$\frac{1}{2}$ & 3 & 1            &1            \\ \hline
 $A_{po}$ &1            & 4 & 1            &1            \\ \hline
\end{tabular}
\end{center}

The meaning of the number in each cell is explained in []. The numbers
themselves are based on our own subjective decisions.

We then get the weight of each factor by calculating the bigest
eigenvalue and it's corresponding eigenvector, as given in Table.

\begin{center}
\begin{tabular}{c|cccc}
  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \hline
  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\
\end{tabular}
\end{center}

We test the consistency of the preferences for this instance of the
AHP. For good consistency [Alonso and Lamata 2006, 446 - 447]:

\begin{itemize}
\item The principal eigenvalue $\lambda_{max}$ of the matrix should be
  close to the number n of alternatives, here 4; we get $\lambda_{max} = 4.047$.
\item The consistency index $CI = (\lambda_{max}-n)/(n-1)$ should be close to 0; we get $CI = 0.0157$.
\item The consistency ratio $CR = CI/RI$ (where RI is the average
  value of CI for random matrices) should be less than 0.1; we get $CR
  = 0.0182$.
\end{itemize}

Hence, our decision method displays perfectly acceptable consistency
and the weights are reasonable.

\subsection{Social Network Model}
\label{sec:social-network-model}

The social network model contains a directed weighted graph $G(V,E)$
in which $V$ denote the employees and $E$ denote the connection
between employees. Since there are personnel changes, $G(V,E)$ will
change with time goes by. In order to simulate this situation, we use
$G_t(V_t,E_t)$ instead of $G(V,E)$ where $t$ is a discrete
variable. So $G_t(V_t,E_t)$ denote the social network in the $t$-th
month.

First, we explain the way we build edges of $G_t(V_t,E_t)$.

When $t = 0$, there are about $370 \times 85\%$ nodes (employees) in
$G_t$. We build edges between employees in the same division or
office, since employees in the same division or office certainly know
each other. So each division or office form a complete graph and
employees in the differient division or office don't know others,
which is impossible. To solve this problem, we build 10 edges for each
employee with employees in other divisions with equal
probability. Then we build the other edges with probability
$p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
    N_{j,t}\right|}$
which is called Jaccard similarity coefficient[Jaccard 1901].

When $t > 0$, there will be employees leaving or joining the
company. If an employee leave, all his edges with other employees with
be deleted. If an employee newly join the company, he will follow
steps which employees at $t = 0$ take. This is the dynamic process of
graph $G_t(V_t,E_t)$.

Let $s_{ij,t}$ denote the weight from $i$ to $j$ at time $t$. We have
these properties of $G_t(V_t,E_t)$:

\begin{itemize}
\item $s_{ij,t} \ne s_{ij,t}$

  We made this graph directed and weighted because one person may
  consider another person his best friend while that person doesn't
  consider him a good friend. This situation may appear because of the
  relationship between superior and subordinate and the relationship
  between person with more friend and person with less friend. In
  general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.

\item $s_{ij,t}=\dfrac{a_{ij,t}+f_{ij,t}}{2}$

  $a_{ij,t}$ denote the influence caused by the relationship between
  superior and subordinate, $f_{ij,t}$ denote the influence caused by
  the amount of friends for $i$ and $j$. We define
$$a_{ij,t}=\begin{cases}
  \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
  1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
\end{cases}$$
, where $L_{i,t}$ denote the level of $i$ at time $t$, and
$$f_{ij,t}=\frac{\left|N_{i,t} \cap
    N_{j,t}\right|}{\left|N_{i,t}\right|}$$.

\end{itemize}

Finally, we explain the concept of clustering coefficient [Duncan
J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
is a measure of the degree to which nodes in a graph tend to cluster
together. $c_{i,t}$ is defined as:

$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
where
$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
$k_{i,t}=\left| N_{i,t} \right|$.

\subsection{Promote and Churn Model}
\label{sec:promote-and-churn-model}

The main part of our model is the algorithm which controls the
behavior of employees. According to assumption 1 and assumption 2, we
have the methodology as follow:

\begin{itemize}
\item [\textit{step 1}]
\end{itemize}

The network of the company we've built changes in terms of
orgnizational churn and promotion. Considering various of factors in
reality, we build an orgnizational churn and promotion model to
predict the dynamic process.

The first part of the model is churn model.We define the churn rate of
an employee $i$ as $l_i$ to evaluate the probability to churn. $l_i$ is
usually controlled by sorts of factors to different degrees. We
divides $l_i$ into three parts:$l_{i1}$, $l_{i2}$ and$l_{i3}$.  $l_{i1}$
represents the churn rate because of lacking of promotion
opportunity. $l_{i2}$ represents the churn rate because of the changes
of other employees related to employee $i$. To simplify our model, we
presume that $l_i1$, $l_i2$ is linear correlated with $(1-p_i)$ and
$s_i$, which means

\begin{equation}
  l_{i1}=\lambda_1(1-p_i),l_{i2}=\lambda_2s_i
\end{equation}

$\lambda_1$ and $\lambda_2$ could be ensured in later calculation.

$l_{i3}$ represents the other factors we can't get any information from
the known conditons so that we regard it as stable.  Thus

\begin{equation}
  l_i = \lambda_1(1-p_i) + \lambda_2s_i +l_i3
\end{equation}

After analyzing a great deal of churn rate reports, we get the
composition of the three parts are 10.9\%, 2.2\% and 75.4\%
respectively. According to the percentage and the general
churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
$l_{i3}$. As an orinigal condition,it satisfies

\begin{equation}
\begin{cases}
  \lambda_1 \sum_{i=1}^{370}(1-p_i) & = 10.9\% \times 370 \times 1.5\% \\
  \lambda_2 \sum_{i=1}^{370}s_i & = 2.2\% \times 370 \times 1.5\% \\
  l_i3 & =1.5 \% \times 75.4 \%
\end{cases}
\end{equation}

Thus we can use equation (4) to calculate the churn rate $l_i$.

The second part of the model is promotion model aimed to predict the
promotion condition.We define the promotion rate of an employee i as
$p_i$ to evaluate the probability to promote.As a matter of fact,if
there is a vacancy, judging if an employee suits the site involves
work experience and ability.It is essential that he is supposed to
have several years of work experience according to issue 6.If an
employee satisfies the experience condition,it turns out to think
about his ability.Since in people model,each employee's ability is
evaluated by a parameter $A_{D_i}$. For each level of position,it has
an ability standard,as shows in Figure[]. The ability of an employee
are supposed to reach the four standard parameters
respectively,otherwise its $p_i$ is 0.For those who reach the
standard, the promotion probability can be calculated by the equation:
$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ is
employee who have probability to promote.

\section{Performance and Analysis}
\label{sec:performance-and-analysis}

\subsection{Analysis for Task 2}
\label{sec:analysis-for-task-2}

a

\subsection{Analysis for Task 3}
\label{sec:analysis-for-task-3}

We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company. With these two assumption, results can be drawn according to our model through simulation.

Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.

\begin{tabular}{*{4}{c}}\toprule[2pt]
Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
\end{tabular}

\subsection{Analysis for Task 4}
\label{sec:analysis-for-task-4}

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_p.pdf}\\
  \caption{Status of positions}\label{t4_p}
\end{figure}

To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints. We execute our program 100 times for each churn rate and average the predicted values. Figure \ref{t4_p} shows the averaged results our model predicted. Under all of these three conditions, the number of employees in the company keeps rising. The higher the churn rate, the lower the final full rate the company reaches after two years. But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_r.pdf}\\
  \caption{Recruiting budget}\label{t4_r}
\end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=7cm]{task4_t.pdf}
  \includegraphics[width=7cm]{task4_s.pdf}\\
  \caption{Training budget and salary budget}\label{t4_t_s}
\end{figure}
The churn rate effect the budget of the company as well. The three parts of the bugdet behave differently when churn rate increases. The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}. Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart. It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.

To maintain enough employees, the company has to spend more on recruiting. So high turnover rate directly increase the recruiting budget. High turnover rate's effect on training budget and salary budget is more complex. On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate. On the other hand, the vacancies in lower level remains low because of the short recruiting time. So the full rate of the company decreases when churn rate rises. Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
\subsection{Analysis for Task 5}
\label{sec:analysis-for-task-5}

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task5_p.pdf}\\
  \caption{Status of position}\label{t5_p}
\end{figure}
We apply following changes to our model to simulate the required process:\\
\begin{itemize}
\item Change the churn rate of junior managers and experienced supervisors to 30\%
\item Prohit external recruiting
\item Promoting only qualified employees
\end{itemize}
\begin{table}
	\begin{center}
		\begin{tabular}{l|cc}\toprule[2pt]
		\bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
		Senior manager/Executive & 5.6 & 8.4\\
		Junior manager/Executive & 9.0 & 18.4\\
		Experienced supervisor & 7.4 & 23.0\\
		Inexperienced supervisor & 9.2 & 23.2\\
		Experienced employee & 72.6 & 107.4\\
		Inexperienced employee & 99.6 & 149.6\\
		Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
		\end{tabular}
		\caption{Status of position}\label{t5_p_t}
	\end{center}
\end{table}

The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}. All the data shown is an average of ten predictions. While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.

We list specific data of each level in Table \ref{t5_p_t}. In the modified case, the numbers of employees are lower than original case especially the those of middle levels. Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave. Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low. The situation given in that task 5 will cause unrecoverable damage to ICM's HR health. With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.

\section{Advice for HR}
\label{sec:advice-for-hr}

a

\subsection{Incentive Mechanism}
\label{sec:incentive-machanism}

a

\subsection{Matching Employees to the Right Position}
\label{sec:matching-employees-to-the-right-position}

a

\section{Team Science}
\label{sec:team-science}

a

\section{Sensitivity Analysis}
\label{sec:sensitivity-analysis}

a

\section{Strengths and Weaknesses}
\label{sec:strengths-and-weaknesses}

\subsection*{Strengths}
\label{sec:strengths}

\begin{itemize}
\item Our model make fully use of the theory of multilayer networks so
  that it quantizes the relation accurately and reasonablly.
\item Our model exellently proves the interaction among these
  factors:leave probability, promotion probability and productivity.
\item The network we built include both microcosmic part and
  macrocosmic part, and they react to each other.
\item Our model proves the effection of time.
\end{itemize}

\subsection*{Weaknesses}
\label{sec:weaknesses}

\begin{itemize}
\item Limited by the time,we neglected sorts of factors which are not so significant.In fact, the model still has space to be perfected.
\item The result has some randomness.
\end{itemize}

\section{Conclusions}
\label{sec:conclusions}

a

% the reference
\begin{thebibliography}{99}

\bibitem{}

\end{thebibliography}

\label{LastPage}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2016-02-01 Tex/paper.tex
test 123
delete 123
add 456
789
delete 456 789
delete 456

@@
 improve it, we build a human capital model based on Social Network
-Analysis and Markov process. 456
+Analysis and Markov process.
 
@@
 \label{sec:restatement-of-the-problem}
-
+We are required to build a mathematical model to solve the problem of heating water in bathtub. Thus we have some subproblems:
+\begin{itemize}
+\item Build a basic model that demonstrate the change of the temperature in the bathtub in space and time without other intervention.
+\item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
+\item Propose a strategy to keep the temperature as even as possible.
+\end{itemize}
+In the first step, we build the simplest model.
+The shape of the bathtub is a cuboid, and the person will stay still.
+In the second step, the person move slowly and the shape of the bathtub changes.
+In the third step, we develop the conclusion of the  strategy.
 \subsection{Literature Review}
@@
 
+In our model, five parts accounts for heat transfer of water: heat exchange between water and air, heat
+exchange between water and the person, heat exchange between water and the bathtub, heat of hot water from the
+faucet and heat of water flow outside. According to thermology, we conduct the equation
+of water temperature in the bathtub. The initial-boundary value condition could be conducted according to
+Fourier theorem, vaporization equation[ ].
+
+Since the equation is a relatively complex 3D partial differential equation, we use matlab to solve it.
+We build a geometry as the bathtub. By finite element method, the geometry discrete into several parts.
+The solution of each part is considered to be a relatively precise value solution.
+
 Definitions of symbols employed in this paper are listed in
@@
 \begin{table}
-\begin{tabular}{|l|l|}
+\begin{tabular}{l|l}
+  Constant & Description \\
+  \hline
+  $k$            &Thermal conductivity of water \\
+  $\rho$         &Density of water \\
+  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
+  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
+  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
+  $C_w$          &Specific heat capacity of water \\
+  $V$            &Total volume of water \\
+  $x_s$          &Humidity ratio in saturated air \\
+  $x_0$          &Initial humidity ratio in the air \\
+  $A$            &Square of water surface \\
+  $V_a$          &Volume of surrounding air \\
+  $C_v$          &Evaporation heat of water \\
+  $u_2$          &Temperature of person's surface \\
+
   Variable & Description \\
   \hline
-  $i$            &Index of an employee \\
-  $L_{i,t}$          &The level of $i$ \\
-  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
-  $a_{ij,t}$        &Represent the influence caused by relationship
-                    between superior and subordinate \\
-  $f_{ij,t}$        &Represent the influence caused by relationship
-                    between person with many friends and person with
-                    few friends \\
-  $c_{i,t}$        &Clustering Coefficient of $i$
+  $u$            &Temperature of water \\
+  $u_1$          &Temperature of air \\
+  $u_3$          &Temperature of bathtub \\
 \end{tabular}
@@
 
-\subsection{Human Performance Model}
-\label{sec:human-model}
+\subsection{Heat Equation}
+\label{sec:heat equation}
 
-In this part, we buid a people model to evaluate an employee in four
-aspects, in terms of \textbf{Quantitative Management Performance} ---
-work achievement, work ability, work attitude and potential. These
-four aspects are supposed to be quantized according to annual
-evaluation based on performance as judged by the supervisor and we
-take these independent variables as $A_{ac_i}$, $A_{ab_1}$, $A_{at_i}$
-and $A_{po_i}$ for each employee $i$. For each of the four parameters,
-it goes from 0 to 1. The statues are used for calculating the
-probability that employee can promote. Meanwhile, they influence
-leaving probability and team cohesiveness as well.
+In this part, we use physical theorem to conduct the heat conduction equation
+in the bathtub.
 
-It is obvious that some of the parameters are somehow more important
-than others. So in an effort to make our model more accurate and
-reliable,we introduce a weighted index of deviation $AD_i$, with
+Figure 1 shows thermal analysis of water in bathtub.
+
+First,we assume that the heat change of all water in a tiny time $\Delta t$ is $\Delta Q$.
+As shown in Figure 1, water in the bathtub have heat exchange with air, the person, and the bathtub.
+In addition, heat changes when the hot water flow in and the excess water flow out.
+Thus $\Delta Q$ is divided into five parts, i.e.
 \begin{equation}
-  A_i=w_{ac} \cdot A_{ac_i} + w_{ab} \cdot A_{ab_i} + w_{at} \cdot A_{at_i} +
-  w_{po} \cdot A_{po_i}
+ \Delta Q=\Delta Q_1+\Delta Q_2-\Delta Q_3-\Delta Q_4
+\end{equation}
+in which $\Delta Q_1$ is heat transferred from air, person and bathtub,
+$\Delta Q_2$ is the heat of the hot water from the faucet in $\Delta t$,
+$\Delta Q_3$ is the heat of the water flow away in $\Delta t$,
+$\Delta Q_4$ is the heat loss of vaporization.
+
+Totally, internal energy of water changes while heat changes.
+Then the temperature changes with
+\begin{equation}
+ 1
 \end{equation}
 
-We determine weights via the Analytical Hierarchy Process(AHP) [Saaty
-1982]. We build a $4 \times 4$ reciprocal matrix by pair comparison:
-\begin{center}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-       &$A_{ac}$      &$A_{ab}$  &$A_{at}$    &$A_{po}$  \\ \hline
- $A_{ac}$ & 1           & 5 & 2            &1            \\ \hline
- $A_{ab}$ &$\frac{1}{5}$ & 1 &$\frac{1}{3}$ & $\frac{1}{4}$\\ \hline
- $A_{at}$ &$\frac{1}{2}$ & 3 & 1            &1            \\ \hline
- $A_{po}$ &1            & 4 & 1            &1            \\ \hline
-\end{tabular}
-\end{center}
+Considering the right side of equation 1.
+Fourier theorem indicates that,
+\begin{equation}
+ dQ=-k\frac{\vartheta u}{\vartheta n}dSdt
+\end{equation}
+holds for the heat flow along a surface with square of dS.
+In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$
+is the derivative of u along the normal line. Thus, after integration of dQ by time and
+space
+\begin{equation}
+ \Delta Q_1=int_{t_1}^{t_2}[{int_{\Gamma}}k\frac{\vartheta u}{\vartheta n}dS]dt
+\end{equation}
+The heat flow into the water by thermal conduction could be calculated by this equation.
 
-The meaning of the number in each cell is explained in []. The numbers
-themselves are based on our own subjective decisions.
+$\Delta Q_2$ is determined by the internal energy of hot water from the faucet in $\Delta t$.
+And $\Delta Q_2$ can be calculated by
+$\Delta Q_2={\Delta m}C{u_h}$.
+Since the hot water is constant,
+$\Delta m=v{\Delta t}$.
 
-We then get the weight of each factor by calculating the bigest
-eigenvalue and it's corresponding eigenvector, as given in Table.
+It is obvious that the excess water is as the same value of hot water in any time period.
+Thus $\Delta Q_3$ can be calculated by
+$\Delta Q_3={\Delta m}Cu$.
+Also, $\Delta m=v{\Delta t}$.
 
-\begin{center}
-\begin{tabular}{c|cccc}
-  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \hline
-  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\
-\end{tabular}
-\end{center}
+According to thermal theorem, heat loss in vaporization is proportional to
+the weight of vapor water.
+$\Delta Q_4={C_v}\Delta {m_v}$.
 
-We test the consistency of the preferences for this instance of the
-AHP. For good consistency [Alonso and Lamata 2006, 446 - 447]:
+Since water could be considered as manifold, according to Green formula,
+\begin{equation}
+ 2
+\end{equation}.
 
-\begin{itemize}
-\item The principal eigenvalue $\lambda_{max}$ of the matrix should be
-  close to the number n of alternatives, here 4; we get $\lambda_{max} = 4.047$.
-\item The consistency index $CI = (\lambda_{max}-n)/(n-1)$ should be close to 0; we get $CI = 0.0157$.
-\item The consistency ratio $CR = CI/RI$ (where RI is the average
-  value of CI for random matrices) should be less than 0.1; we get $CR
-  = 0.0182$.
-\end{itemize}
+Combining the equations above,
+\begin{equation}
+ 3
+\end{equation}.
+Some parameters would be discussed in the following sections.
 
-Hence, our decision method displays perfectly acceptable consistency
-and the weights are reasonable.
+\subsection{Initial-Boundary Value Condition}
+\label{initial-boundary value condition}
 
-\subsection{Social Network Model}
-\label{sec:social-network-model}
+Boundary value condition is quite essential in partial differential equations. In our model, water is not a regular research object.
+Thus boundary value condition is complex.
 
-The social network model contains a directed weighted graph $G(V,E)$
-in which $V$ denote the employees and $E$ denote the connection
-between employees. Since there are personnel changes, $G(V,E)$ will
-change with time goes by. In order to simulate this situation, we use
-$G_t(V_t,E_t)$ instead of $G(V,E)$ where $t$ is a discrete
-variable. So $G_t(V_t,E_t)$ denote the social network in the $t$-th
-month.
+The boundary of water consists of three parts: water-air boundary, water-person boundary, and water-bathtub boundary. We denote them as
+${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$ respectively.
 
-First, we explain the way we build edges of $G_t(V_t,E_t)$.
+Since person is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
+as the Dirichlet value condition. That is
+\begin{equation}
+ u=u_2, (x,y,z)\in {\Gamma}_2
+\end{equation}.
 
-When $t = 0$, there are about $370 \times 85\%$ nodes (employees) in
-$G_t$. We build edges between employees in the same division or
-office, since employees in the same division or office certainly know
-each other. So each division or office form a complete graph and
-employees in the differient division or office don't know others,
-which is impossible. To solve this problem, we build 10 edges for each
-employee with employees in other divisions with equal
-probability. Then we build the other edges with probability
-$p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
-    N_{j,t}\right|}$
-which is called Jaccard similarity coefficient[Jaccard 1901].
+The boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered as the third boundary value condition approximately. That is
+\begin{equation}
+ k\frac{\vartheta u}{\vartheta n}+{{\gamma}_i}u={{\gamma}_i}{u_i}, (x,y,z)\in {\Gamma}_i
+\end{equation}.
+In the equation, i=1,3, and $u_i$ is the temperature of contact material,
+${\gamma}_i$ is the heat exchange coefficient of ${\Gamma}_i$.
 
-When $t > 0$, there will be employees leaving or joining the
-company. If an employee leave, all his edges with other employees with
-be deleted. If an employee newly join the company, he will follow
-steps which employees at $t = 0$ take. This is the dynamic process of
-graph $G_t(V_t,E_t)$.
+In our model, the initial value condition is the initial temperature of water. We assume the temperature is equilibrium throughout the bathtub.
 
-Let $s_{ij,t}$ denote the weight from $i$ to $j$ at time $t$. We have
-these properties of $G_t(V_t,E_t)$:
+\subsection{PDE Solve}
 
-\begin{itemize}
-\item $s_{ij,t} \ne s_{ij,t}$
-
-  We made this graph directed and weighted because one person may
-  consider another person his best friend while that person doesn't
-  consider him a good friend. This situation may appear because of the
-  relationship between superior and subordinate and the relationship
-  between person with more friend and person with less friend. In
-  general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.
-
-\item $s_{ij,t}=\dfrac{a_{ij,t}+f_{ij,t}}{2}$
-
-  $a_{ij,t}$ denote the influence caused by the relationship between
-  superior and subordinate, $f_{ij,t}$ denote the influence caused by
-  the amount of friends for $i$ and $j$. We define
-$$a_{ij,t}=\begin{cases}
-  \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
-  1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
-\end{cases}$$
-, where $L_{i,t}$ denote the level of $i$ at time $t$, and
-$$f_{ij,t}=\frac{\left|N_{i,t} \cap
-    N_{j,t}\right|}{\left|N_{i,t}\right|}$$.
-
-\end{itemize}
-
-Finally, we explain the concept of clustering coefficient [Duncan
-J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
-is a measure of the degree to which nodes in a graph tend to cluster
-together. $c_{i,t}$ is defined as:
-
-$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
-    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
-where
-$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
-$k_{i,t}=\left| N_{i,t} \right|$.
-
-\subsection{Promote and Churn Model}
-\label{sec:promote-and-churn-model}
-
-The main part of our model is the algorithm which controls the
-behavior of employees. According to assumption 1 and assumption 2, we
-have the methodology as follow:
-
-\begin{itemize}
-\item [\textit{step 1}]
-\end{itemize}
-
-The network of the company we've built changes in terms of
-orgnizational churn and promotion. Considering various of factors in
-reality, we build an orgnizational churn and promotion model to
-predict the dynamic process.
-
-The first part of the model is churn model.We define the churn rate of
-an employee $i$ as $l_i$ to evaluate the probability to churn. $l_i$ is
-usually controlled by sorts of factors to different degrees. We
-divides $l_i$ into three parts:$l_{i1}$, $l_{i2}$ and$l_{i3}$.  $l_{i1}$
-represents the churn rate because of lacking of promotion
-opportunity. $l_{i2}$ represents the churn rate because of the changes
-of other employees related to employee $i$. To simplify our model, we
-presume that $l_i1$, $l_i2$ is linear correlated with $(1-p_i)$ and
-$s_i$, which means
-
-\begin{equation}
-  l_{i1}=\lambda_1(1-p_i),l_{i2}=\lambda_2s_i
-\end{equation}
-
-$\lambda_1$ and $\lambda_2$ could be ensured in later calculation.
-
-$l_{i3}$ represents the other factors we can't get any information from
-the known conditons so that we regard it as stable.  Thus
-
-\begin{equation}
-  l_i = \lambda_1(1-p_i) + \lambda_2s_i +l_i3
-\end{equation}
-
-After analyzing a great deal of churn rate reports, we get the
-composition of the three parts are 10.9\%, 2.2\% and 75.4\%
-respectively. According to the percentage and the general
-churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
-$l_{i3}$. As an orinigal condition,it satisfies
-
-\begin{equation}
-\begin{cases}
-  \lambda_1 \sum_{i=1}^{370}(1-p_i) & = 10.9\% \times 370 \times 1.5\% \\
-  \lambda_2 \sum_{i=1}^{370}s_i & = 2.2\% \times 370 \times 1.5\% \\
-  l_i3 & =1.5 \% \times 75.4 \%
-\end{cases}
-\end{equation}
-
-Thus we can use equation (4) to calculate the churn rate $l_i$.
-
-The second part of the model is promotion model aimed to predict the
-promotion condition.We define the promotion rate of an employee i as
-$p_i$ to evaluate the probability to promote.As a matter of fact,if
-there is a vacancy, judging if an employee suits the site involves
-work experience and ability.It is essential that he is supposed to
-have several years of work experience according to issue 6.If an
-employee satisfies the experience condition,it turns out to think
-about his ability.Since in people model,each employee's ability is
-evaluated by a parameter $A_{D_i}$. For each level of position,it has
-an ability standard,as shows in Figure[]. The ability of an employee
-are supposed to reach the four standard parameters
-respectively,otherwise its $p_i$ is 0.For those who reach the
-standard, the promotion probability can be calculated by the equation:
-$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ is
-employee who have probability to promote.
-
-\section{Performance and Analysis}
+\section{Results and Analysis}
 \label{sec:performance-and-analysis}
@@
 \begin{itemize}
-\item Limited by the time,we neglected sorts of factors which are not so significant.In fact, the model still has space to be perfected.
-\item The result has some randomness.
+\item We assume that the water is still. In fact, streams flow and fluid dynamic is better taken into consideration. The actual situation is much complicated.
+\item The model of the person should be more realistic. In fact, model of human body includes hands, legs or other parts, and the surface of human skin isn't even.
+\item The condensation of water should be taken into consideration. Water that evaporate become water vapour, and some will condense into water on the bathtub.
 \end{itemize}

### 2016-02-01 Tex/paper.tex
aa

--- 2016-01-31 Tex/paper.tex
@@
 improve it, we build a human capital model based on Social Network
-Analysis and Markov process. 456
+Analysis and Markov process.
+
+\begin{displaymath}
+Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
+\end{displaymath}
+
+\begin{displaymath}
+\begin{aligned}
+\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
+\end{aligned}
+\end{displaymath}
+
+\begin{displaymath}
+\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{}
+\end{displaymath}
 

### 2016-02-01 Tex/paper.tex

--- 2016-02-01 Tex/paper.tex
@@
 Analysis and Markov process.
+
+\begin{displaymath}
+Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
+\end{displaymath}
+
+\begin{displaymath}
+\begin{aligned}
+\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
+\end{aligned}
+\end{displaymath}
+
+\begin{displaymath}
+\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{}
+\end{displaymath}
 

### 2016-02-01 Tex/paper.tex
laws added
123

@@
 \label{sec:introduction}
-
-Considering the shortage of the talent, it's essential for companys to
-retain good people and make them well-trained. However, current
-situation is not satisfactory while many talents always tend to get a
-good job via job-hopping, causing orgnizational churn in employees who
-are closely connected to them. In order to simulate this process and
-improve it, we build a human capital model based on Social Network
-Analysis and Markov process.
-
 \begin{displaymath}
@@
 \begin{displaymath}
-\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{}
+\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
 \end{displaymath}
@@
 In the third step, we develop the conclusion of the  strategy.
-\subsection{Literature Review}
-\label{sec:literature-review}
-
-\begin{itemize}
-\item
-\item
-\item
-\end{itemize}
-
-\section{Terminology}
-\label{sec:terminology}
-
-\begin{itemize}
-\item
-\item
-\item
-\end{itemize}
 
@@
 % the main section of the paper
-\section{Human Capital Model}
+\section{Water in the Bathtub Model}
 \label{sec:human-capital-model}
-
-\subsection{Model Overview}
-\label{sec:model-overview}
-
-Partial differential equations are widely used in natural science, engineering and economical management.
-It is natural to use partial differential equation to solve this physical problem.
-
-In our model, five parts accounts for heat transfer of water: heat exchange between water and air, heat
-exchange between water and the person, heat exchange between water and the bathtub, heat of hot water from the
-faucet and heat of water flow outside. According to thermology, we conduct the equation
-of water temperature in the bathtub. The initial-boundary value condition could be conducted according to
-Fourier theorem, vaporization equation[ ].
-
-Since the equation is a relatively complex 3D partial differential equation, we use matlab to solve it.
-We build a geometry as the bathtub. By finite element method, the geometry discrete into several parts.
-The solution of each part is considered to be a relatively precise value solution.
-
 Definitions of symbols employed in this paper are listed in
@@
 
+\subsection{Model Overview}
+\label{sec:model-overview}
+
+Partial differential equations are widely used in natural science, engineering and economical management.
+It is natural to use partial differential equation to solve this physical problem.
+
+In our model, five parts accounts for heat transfer of water: heat exchange between water and air, heat
+exchange between water and the person, heat exchange between water and the bathtub, heat of hot water from the
+faucet and heat of water flow outside. According to thermology, we conduct the equation
+of water temperature in the bathtub. The initial-boundary value condition could be conducted according to
+Fourier theorem, vaporization equation[ ].
+
+Since the equation is a relatively complex 3D partial differential equation, we use matlab to solve it.
+We build a geometry as the bathtub. By finite element method, the geometry discrete into several parts.
+The solution of each part is considered to be a relatively precise value solution.
+
 \subsection{Heat Equation}
@@
 \begin{equation}
- 1
+ Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
 \end{equation}
+, in which $\Omega$ is the region of water, $\rho$ is the density of water, $u_f$ is the final temperature when t=$t_2$, $u_i$ is the initial temperature when t=$t_1$.
 
@@
 \end{equation}
-holds for the heat flow along a surface with square of dS.
-In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$
-is the derivative of u along the normal line. Thus, after integration of dQ by time and
-space
+holds for the heat flow through surface with square of dS.
+In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
 \begin{equation}
@@
 \end{equation}
-The heat flow into the water by thermal conduction could be calculated by this equation.
+in which $\Gamma$ is the boundary of $\Omega$.
+The heat flow into the water by thermal conduction could be calculated by the equation.
 
@@
 Thus $\Delta Q_3$ can be calculated by
-$\Delta Q_3={\Delta m}Cu$.
+$\Delta Q_3={\Delta m}{C_w}u$.
 Also, $\Delta m=v{\Delta t}$. 
+$\Delta v$ is the weight of hot water each second, $\Delta m$ is the weight of hot water in $\Delta t$.
 
@@
 $\Delta Q_4={C_v}\Delta {m_v}$.
+$\Delta {m_v}$ is the weight of evaporation water in $\Delta t$, $\Delta {C_v}$ is evaporation heat of water.
 
@@
 \begin{equation}
- 2
+ \int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
 \end{equation}.
@@
 \begin{equation}
- 3
+ \rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
 \end{equation}.
-Some parameters would be discussed in the following sections.
+In this heat equation, $u_h$ and $v_h$ are two variables that control the strategy.
+
+Now discuss g, evaporation rate per square. According to empirical formula in [], we know that
+\begin{equation}
+ g=\frac{(25+19v)({x_s}-x)}{3600}
+\end{equation}
+in which v is the velocity of air, ${x_s}$ is humidity ratio in saturated air, $x$ is humidity ratio in air. 
+Considering the water vapor rate in the air, it indicates 
+\begin{equation}
+ x=x_0+\int \frac{Ag}{\rho V_a}dt
+\end{equation}
+in which, $x_0$ is the initial humidity ratio in the air, $\rho$ is density of water, $V_a$ is the total air volume of surrounding air.
+
+Combing the two equations and differentiating, we get a ordinary partial equation 
+\begin{equation}
+ \frac{3600}{25+19v} \frac{dg}{dt}=\frac{A}{\rho {V_a}}
+\end{equation}
+Solving the equation, we get the solution 
+\begin{equation}
+ g=\frac{(25+19v)({x_s}-{x_0})}{3600}e^{-\lambda t}, \lambda =\frac{A(25+19v)}{3600\rho {V_a}}
+\end{equation}
 
@@
 
-In our model, the initial value condition is the initial temperature of water. We assume the temperature is equilibrium throughout the bathtub.
+In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It would take several steps to calculate them.
+
+Consider the temperature of air, $u_1$. Heat change of air consists of two aspects, heat conduction and evaporation.
+
+In our model, we assume the temperature of water is equilibrium throughout the bathtub initially.
 
 \subsection{PDE Solve}
+\label{sec:PDE solve}
+Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this problem.
+
+We use Partial Differential Equation Toolbox in matlab to solve our equations.
+Partial Differential Equation Toolbox makes use of finite element method to discrete irregular geometry and calculate a relatively precise solution.
+get solution of temperature corresponding to different $u_h$ and $v_h$.
+By comparing temperature distribution, we choose proper parameters as the best strategy.
+
+First, we build a 3D geometry model to simulate a proper-size bathtub, as shown in Figure 2. Matlab divided the geometry into several elements.
+
+Then we input the heat equation and initial-boundary value conditions. Boundary value conditions are different in three parts.
 
@@
 
-\subsection{Analysis for Task 2}
-\label{sec:analysis-for-task-2}
-
-a
-
-\subsection{Analysis for Task 3}
-\label{sec:analysis-for-task-3}
-
-We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company.
-With these two assumption, results can be drawn according to our model through simulation.
-
-Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.
-
-\begin{tabular}{*{4}{c}}\toprule[2pt]
-Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
-1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
-\end{tabular}
-
-\subsection{Analysis for Task 4}
-\label{sec:analysis-for-task-4}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task4_p.pdf}\\
-  \caption{Status of positions}\label{t4_p}
-\end{figure}
-
-To analyze the status of positions under different churn rate, we use our model to simulate dynamic processes with these churn rate constraints.
-We execute our program 100 times for each churn rate and average the predicted values.
-Figure \ref{t4_p} shows the averaged results our model predicted.
-Under all of these three conditions, the number of employees in the company keeps rising.
-The higher the churn rate, the lower the final full rate the company reaches after two years.
-But ICM can sustain its 80\% for positions even if the churn rate goes to 35\% according to our model's precition.
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task4_r.pdf}\\
-  \caption{Recruiting budget}\label{t4_r}
-\end{figure}
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=7cm]{task4_t.pdf}
-  \includegraphics[width=7cm]{task4_s.pdf}\\
-  \caption{Training budget and salary budget}\label{t4_t_s}
-\end{figure}
-The churn rate effect the budget of the company as well.
-The three parts of the bugdet behave differently when churn rate increases.
-The calculated budget is shown in Figure \ref{t4_r} and Figure \ref{t4_t_s}.
-Each data point in three charts is an averaged result of 10 predictions and a linear trendline is added to each chart.
-It is clear that recruiting budget showed in Figure \ref{t4_r} is likely to be proportional to the churn rate while salary budget and training budget showed in Figure \ref{t4_t_s} are likely to be inversely proportional to the churn rate.
-
-To maintain enough employees, the company has to spend more on recruiting.
-So high turnover rate directly increase the recruiting budget.
-High turnover rate's effect on training budget and salary budget is more complex.
-On the one hand, when churn rate goes up, vacancies in the middle level keeps rising due to long recruiting time and low promote rate.
-On the other hand, the vacancies in lower level remains low because of the short recruiting time.
-So the full rate of the company decreases when churn rate rises.
-Since training budget and salary budget are closely related to full rate, both of them decrease when turnover rate goes up.
-\subsection{Analysis for Task 5}
-\label{sec:analysis-for-task-5}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=10cm]{task5_p.pdf}\\
-  \caption{Status of position}\label{t5_p}
-\end{figure}
-We apply following changes to our model to simulate the required process:\\
-\begin{itemize}
-\item Change the churn rate of junior managers and experienced supervisors to 30\%
-\item Prohit external recruiting
-\item Promoting only qualified employees
-\end{itemize}
-\begin{table}
-	\begin{center}
-		\begin{tabular}{l|cc}\toprule[2pt]
-		\bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
-		Senior manager/Executive & 5.6 & 8.4\\
-		Junior manager/Executive & 9.0 & 18.4\\
-		Experienced supervisor & 7.4 & 23.0\\
-		Inexperienced supervisor & 9.2 & 23.2\\
-		Experienced employee & 72.6 & 107.4\\
-		Inexperienced employee & 99.6 & 149.6\\
-		Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
-		\end{tabular}
-		\caption{Status of position}\label{t5_p_t}
-	\end{center}
-\end{table}
-
-The result of simulation is shown in Figure \ref{t5_p} and Table \ref{t5_p_t}.
-All the data shown is an average of ten predictions.
-While the number of positions occupied remains stable with origial conditions, it drops remarkably with modified conditions.
-
-We list specific data of each level in Table \ref{t5_p_t}.
-In the modified case, the numbers of employees are lower than original case especially the those of middle levels.
-Since there is no external recruiting in modified case, it is obivious that the full rate will decrease due to employees' leave.
-Although some qualified employees can be promoted into higher level, the high churn rate of the middle level and difficulty of satisfying the promotion conditions make the numbers of middle level employees relatively low.
-The situation given in that task 5 will cause unrecoverable damage to ICM's HR health.
-With the full rate of middle level employees lower than 50\%, the HR structure is broken into fragments and the company won't be able to function normally.
-
-\section{Advice for HR}
-\label{sec:advice-for-hr}
-
-a
-
-\subsection{Incentive Mechanism}
-\label{sec:incentive-machanism}
-
-a
-
-\subsection{Matching Employees to the Right Position}
-\label{sec:matching-employees-to-the-right-position}
-
-a
-
-\section{Team Science}
-\label{sec:team-science}
-
-a
-
 \section{Sensitivity Analysis}
@@
 
-a
+\subsection{Parameters of Bathtub}
+\label{sec:parameters of bathtub}
+\begin{itemize}
+\item
+\item
+\end{itemize}
+
+\subsection{Parameters of Person}
+\label{sec:parameters of person}
+\begin{itemize}
+\item
+\item
+\item
+\end{itemize}
+
+\subsection{Effects of Motion}
+\label{sec:effects of motion}
+
+\subsection{Effects of Bubble Bath Additive}
+\label{sec:effects of bubble bath additive}
 
@@
 \begin{itemize}
-\item Our model make fully use of the theory of multilayer networks so
-  that it quantizes the relation accurately and reasonablly.
-\item Our model exellently proves the interaction among these
+\item Our model make fully use of the theory of multi-layer networks so
+  that it quantizes the relation accurately and reasonably.
+\item Our model excellently proves the interaction among these
   factors:leave probability, promotion probability and productivity.
@@
   macrocosmic part, and they react to each other.
-\item Our model proves the effection of time.
+\item Our model proves the effect of time.
 \end{itemize}
@@
 \end{itemize}
-
-\section{Conclusions}
-\label{sec:conclusions}
-
-a
 

### 2016-02-01 Tex/paper.tex

@@
 \label{sec:introduction}
+\begin{displaymath}
+Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
+\end{displaymath}
+
+\begin{displaymath}
+\begin{aligned}
+\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
+\end{aligned}
+\end{displaymath}
+
+\begin{displaymath}
+\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
+\end{displaymath}
+
 \begin{displaymath}
@@
 
-The boundary of water consists of three parts: water-air boundary, water-person boundary, and water-bathtub boundary. We denote them as
-${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$ respectively.
+The boundary of water consists of four parts: water-air boundary, water-person boundary, water-bathtub boundary, and the square for faucet. We denote them as
+${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$, ${\Gamma}_4$ respectively.
 
@@
 \begin{equation}
- u=u_2, (x,y,z)\in {\Gamma}_2
-\end{equation}.
+ u=u_i, (x,y,z)\in {\Gamma}_i, i=2.4
+\end{equation}
+In the equation, $u_2$ is the surface temperature of person. We assume it is constant. $u_4$ is the temperature of hot water.
 
@@
 
-In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It would take several steps to calculate them.
+In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It takes several steps to calculate them.
 
-Consider the temperature of air, $u_1$. Heat change of air consists of two aspects, heat conduction and evaporation.
+Consider the temperature of air, $u_1$. Heat change of air consists of two ways, heat conduction and evaporation.
 
@@
 \begin{itemize}
-\item
-\item
+\item We change the shape of the bathtub from square to sphere and elliptical with the same strategy.
+The temperature graphic shows that sphere is the most proper shape for keeping water temperature.
+Square performs the worst on keeping temperature.
+However, temperature of square bathtub is more evenly than others.
+\item We change the volume of the bathtub without changing its proportion. The result shows that with the same $v_h$, 
 \end{itemize}

### 2016-02-01 Tex/paper.tex
non-technical explanations added

@@
 
+\section{Non-technical explanation}
+
+Users,
+
+If you'd like to use the bathtub, it's better to acknowledge that:
+
+\begin{itemize}
+\item Obviously, the water exchange thermal energy directly with the air. That's why you can see water vapour float above the water.
+\item On the other hand, the bathtub is cooler than the water on most occasions.
+It's reasonable that the bathtub absorbs heat from the water.
+However, the bathtub conduct heat easily, while in this way the air's temperature rises.
+\end{itemize}
+From statement above, you may understand our bathtub can't stay in a even temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more in your bath :
+\begin{itemize}
+\item To keep the water warm and relax yourself, you may turn the faucet on.
+Water-in in high temperature loses it's energy quickly, and water-in in low temperature is unable to warm your surrounding.
+It's best that you set the speed of the water-in at xxx, and temperature at yyy.
+\item Further more, your movement effects the water.
+It would be great if you stay still, but it doesn't count too much.
+For a better temperature-keeping situation, you may add some bubble bath additive to decrease the temperature loss.
+\end{itemize}
+
 \end{document}

### 2016-02-01 Tex/paper.tex
12

--- 2016-02-01 Tex/paper.tex
@@
 
-First,we assume that the heat change of all water in a tiny time $\Delta t$ is $\Delta Q$.
+First,we assume that the heat change of all water in a tiny time $\Delta t$ from $t_1$ to $t_2$ is $\Delta Q$.
 As shown in Figure 1, water in the bathtub have heat exchange with air, the person, and the bathtub.
@@
 \end{equation}
-holds for the heat flow through surface with square of dS.
+holds for the heat flow through surface with square of dS, as shown in Figure 2.
 In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
@@
 
-According to thermal theorem, heat loss in vaporization is proportional to
-the weight of vapor water.
+According to thermal theorem, heat loss in vaporization is proportional to the weight of vapor water.
 $\Delta Q_4={C_v}\Delta {m_v}$.
@@
 \begin{equation}
- \int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
-& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
-& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
+% \int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+%& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+%& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz%
 \end{equation}.
@@
 \begin{equation}
- \rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
+% \rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}%
 \end{equation}.
@@
 
-Now discuss g, evaporation rate per square. According to empirical formula in [], we know that
+Now discuss g, evaporation rate per square.
+As Figure 3 shows, water evaporate into air and air humidity increases, until it saturate. According to empirical formula in [], we know that
 \begin{equation}
@@
 in which v is the velocity of air, ${x_s}$ is humidity ratio in saturated air, $x$ is humidity ratio in air.
-Considering the water vapor rate in the air, it indicates
+Considering the humidity ratio in the air, it indicates
 \begin{equation}
@@
  k\frac{\vartheta u}{\vartheta n}+{{\gamma}_i}u={{\gamma}_i}{u_i}, (x,y,z)\in {\Gamma}_i
-\end{equation}.
+\end{equation}
 In the equation, i=1,3, and $u_i$ is the temperature of contact material,
@@
 
-\subsection{PDE Solve}
-\label{sec:PDE solve}
+\subsection{PDE Solution}
+\label{sec:PDE solution}
 Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this problem.
@@
 
+Our strategy focus on two variables, $v_h$ and $u_h$. Several pairs of data are tested to find the best strategy.
+\begin{center}
+\begin{tabular}{|c|c|c|}
+\hline
+      &$v_h$  &$u_h$        \\ \hline
+ 1    &             & 5              \\ \hline
+ 2    &             & 1              \\ \hline
+ 3    &             & 3              \\ \hline
+ 4    &             & 4              \\ \hline
+\end{tabular}
+\end{center}
+
 \section{Sensitivity Analysis}
@@
 \begin{itemize}
-\item We change the shape of the bathtub from square to sphere and elliptical with the same strategy.
+\item We change the shape of the bathtub to sphere and elliptical with the same strategy.
 The temperature graphic shows that sphere is the most proper shape for keeping water temperature.
@@
 However, temperature of square bathtub is more evenly than others.
-\item We change the volume of the bathtub without changing its proportion. The result shows that with the same $v_h$, 
+\item We change the volume of the bathtub without changing the proportion.
+The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increased as volume increases.
 \end{itemize}
@@
 \label{sec:effects of motion}
+When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases.
+
+In another aspect, the air above flow, so that evaporation heat of water increases.
 
@@
 \begin{itemize}
-\item Our model make fully use of the theory of multi-layer networks so
-  that it quantizes the relation accurately and reasonably.
-\item Our model excellently proves the interaction among these
-  factors:leave probability, promotion probability and productivity.
+\item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
+\item Our model build a 3D geometry to simulate the research object so 
 \item The network we built include both microcosmic part and

### 2016-02-01 Tex/paper.tex
corrected

@@
 
-In our model, five parts accounts for heat transfer of water: heat exchange between water and air, heat
-exchange between water and the person, heat exchange between water and the bathtub, heat of hot water from the
-faucet and heat of water flow outside. According to thermology, we conduct the equation
-of water temperature in the bathtub. The initial-boundary value condition could be conducted according to
+In our model, five factors account for heat transfer of water: heat exchange between water and air, heat
+exchange between water and the person, heat exchange between water and the bathtub, heat energy of hot water from the
+faucet and heat energy of water flow outside. According to thermology, we deduce the equation
+of water temperature in the bathtub. The initial-boundary value conditions are deduced according to
 Fourier theorem, vaporization equation[ ].
@@
 Since the equation is a relatively complex 3D partial differential equation, we use matlab to solve it.
-We build a geometry as the bathtub. By finite element method, the geometry discrete into several parts.
+We build a geometry as the bathtub. By finite element method, the geometry is divided into several parts.
 The solution of each part is considered to be a relatively precise value solution.
@@
 
-In this part, we use physical theorem to conduct the heat conduction equation
+In this part, we use physical theorem to deduce the heat conduction equation
 in the bathtub.
@@
 
-First,we assume that the heat change of all water in a tiny time $\Delta t$ from $t_1$ to $t_2$ is $\Delta Q$.
-As shown in Figure 1, water in the bathtub have heat exchange with air, the person, and the bathtub.
+First, we assume that the heat change of all the water in a tiny time $\Delta t$ from $t_1$ to $t_2$ is $\Delta Q$.
+As it shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
 In addition, heat changes when the hot water flow in and the excess water flow out.
@@
 \end{equation}
-in which $\Delta Q_1$ is heat transferred from air, person and bathtub,
+in which $\Delta Q_1$ is the heat transferred from air, person and bathtub,
 $\Delta Q_2$ is the heat of the hot water from the faucet in $\Delta t$,
 $\Delta Q_3$ is the heat of the water flow away in $\Delta t$,
-$\Delta Q_4$ is the heat loss of vaporization.
+$\Delta Q_4$ is the heat loss because of vaporization.
 
-Totally, internal energy of water changes while heat changes.
-Then the temperature changes with
+Totally, internal energy of water changes when heat exchanges happen.
+Then the temperature changes according to the equation
 \begin{equation}
@@
 \end{equation}
-, in which $\Omega$ is the region of water, $\rho$ is the density of water, $u_f$ is the final temperature when t=$t_2$, $u_i$ is the initial temperature when t=$t_1$.
+, in which $\Omega$ is the region of water, $\rho$ represents the density of water, $u_f$ stands for the final temperature when t=$t_2$, and $u_i$ is the initial temperature when t=$t_1$.
 
@@
 \begin{equation}
- dQ=-k\frac{\vartheta u}{\vartheta n}dSdt
+ dQ=-k\frac{\partial u}{\partial n}dSdt
 \end{equation}
-holds for the heat flow through surface with square of dS, as shown in Figure 2.
-In the equation, k is thermal conductivity, $\frac{\vartheta u}{\vartheta n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
+holds for the heat flow through surface with square of dS, as it shown in Figure 2.
+In the equation, k is thermal conductivity, $\frac{\partial u}{\partial n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
 \begin{equation}
- \Delta Q_1=int_{t_1}^{t_2}[{int_{\Gamma}}k\frac{\vartheta u}{\vartheta n}dS]dt
+ \Delta Q_1=\int_{t_1}^{t_2}[{\int_{\Gamma}}k\frac{\partial u}{\partial n}dS]dt
 \end{equation}
-in which $\Gamma$ is the boundary of $\Omega$.
-The heat flow into the water by thermal conduction could be calculated by the equation.
+in which $\Gamma$ is the boundary of $\Omega$,
+the heat flow into the water by thermal conduction could be calculated.
 
@@
 
-It is obvious that the excess water is as the same value of hot water in any time period.
+It is obvious that the excess water is the same value of hot water in any time period.
 Thus $\Delta Q_3$ can be calculated by
@@
 Also, $\Delta m=v{\Delta t}$.
-$\Delta v$ is the weight of hot water each second, $\Delta m$ is the weight of hot water in $\Delta t$.
+$\Delta v$ is the weight of hot water per second, $\Delta m$ is the weight of hot water flows in during $\Delta t$.
 
@@
 $\Delta Q_4={C_v}\Delta {m_v}$.
-$\Delta {m_v}$ is the weight of evaporation water in $\Delta t$, $\Delta {C_v}$ is evaporation heat of water.
+$\Delta {m_v}$ is the weight of evaporation water in $\Delta t$, ${C_v}$ is evaporation heat of water per kilogram.
 
-Since water could be considered as manifold, according to Green formula,
+Since water could be considered as manifold, according to Green formula, we deduce the formula
+\begin{displaymath}
+\begin{aligned}
+\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
+& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
+& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
+\end{aligned}
+\end{displaymath}
+
+Combining the equations above, we conclude that
 \begin{equation}
-% \int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
-%& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
-%& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz%
-\end{equation}.
-
-Combining the equations above,
-\begin{equation}
-% \rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}%
-\end{equation}.
+\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}%
+\end{equation}
 In this heat equation, $u_h$ and $v_h$ are two variables that control the strategy.
 
-Now discuss g, evaporation rate per square.
-As Figure 3 shows, water evaporate into air and air humidity increases, until it saturate. According to empirical formula in [], we know that
+Now let's discuss g, evaporation rate per square.
+As Figure 3 shows, water evaporates into air and air humidity increases, until it is saturate. According to empirical formula in [], we know that
 \begin{equation}
@@
 \end{equation}
-in which v is the velocity of air, ${x_s}$ is humidity ratio in saturated air, $x$ is humidity ratio in air.
+in which v is the velocity of air, ${x_s}$ is humidity ratio in saturated air, $x$ is unsaturated humidity ratio in air.
 Considering the humidity ratio in the air, it indicates
@@
 \end{equation}
-in which, $x_0$ is the initial humidity ratio in the air, $\rho$ is density of water, $V_a$ is the total air volume of surrounding air.
+in which $x_0$ is the initial humidity ratio in the air, $\rho$ is the density of water, $V_a$ is the total volume of surrounding air.
 
-Combing the two equations and differentiating, we get a ordinary partial equation
+Combing and differentiating two equations, we get an ordinary partial equation
 \begin{equation}
@@
 
-Boundary value condition is quite essential in partial differential equations. In our model, water is not a regular research object.
+Boundary value conditions are quite essential in partial differential equations. In our model, water is not a regular research object.
 Thus boundary value condition is complex.
@@
 \end{equation}
-In the equation, $u_2$ is the surface temperature of person. We assume it is constant. $u_4$ is the temperature of hot water.
+In the equation, $u_2$ is the surface temperature of the person. We assume it is constant. $u_4$ is the temperature of hot water.
 
@@
 \begin{equation}
- k\frac{\vartheta u}{\vartheta n}+{{\gamma}_i}u={{\gamma}_i}{u_i}, (x,y,z)\in {\Gamma}_i
+ k\frac{\partial u}{\partial n}+{{\gamma}_i}u={{\gamma}_i}{u_i}, (x,y,z)\in {\Gamma}_i
 \end{equation}
-In the equation, i=1,3, and $u_i$ is the temperature of contact material,
+In the equation, i=1 or 3 and $u_i$ is the temperature of contact material,
 ${\gamma}_i$ is the heat exchange coefficient of ${\Gamma}_i$.
 
-In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, they are time-dependant functions. It takes several steps to calculate them.
+In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, and they are time-dependant functions. It takes several steps to calculate them.
 
-Consider the temperature of air, $u_1$. Heat change of air consists of two ways, heat conduction and evaporation.
+Consider the temperature of air, $u_1$. Heat exchange of air consists of two ways, heat conduction and evaporation.
 
@@
 \label{sec:PDE solution}
-Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this problem.
+Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this kind of problem.
 
 We use Partial Differential Equation Toolbox in matlab to solve our equations.
-Partial Differential Equation Toolbox makes use of finite element method to discrete irregular geometry and calculate a relatively precise solution.
-get solution of temperature corresponding to different $u_h$ and $v_h$.
+Partial Differential Equation Toolbox makes use of finite element method to separate irregular geometry and calculate a relatively precise solution, get solution of temperature corresponding to different $u_h$ and $v_h$.
 By comparing temperature distribution, we choose proper parameters as the best strategy.
 
-First, we build a 3D geometry model to simulate a proper-size bathtub, as shown in Figure 2. Matlab divided the geometry into several elements.
+First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure 2. Matlab divided the geometry into several elements.
 

### 2016-02-01 Tex/paper.tex
12

--- 2016-02-01 Tex/paper.tex
@@
 
-Our strategy focus on two variables, $v_h$ and $u_h$. Several pairs of data are tested to find the best strategy.
+Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
 \begin{center}
@@
       &$v_h$  &$u_h$        \\ \hline
- 1    &             & 5              \\ \hline
- 2    &             & 1              \\ \hline
- 3    &             & 3              \\ \hline
- 4    &             & 4              \\ \hline
+ 1    &0.1             & 50              \\ \hline
+ 2    &0.2             & 50              \\ \hline
+ 3    &0.3             & 50              \\ \hline
+ 4    &0.1             & 40              \\ \hline
+ 5    &0.2             & 40              \\ \hline
+ 6    &0.3             & 40              \\ \hline
+ 7    &0.1             & 30              \\ \hline
+ 8    &0.2             & 30              \\ \hline
+ 9    &0.3             & 30              \\ \hline
 \end{tabular}
@@
 \label{sec:effects of motion}
-When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases.
+When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases.
+That means heat exchange between water and person increases.
+In another aspect, the air above flow, so that evaporation heat of water increases.
+Water losses more heat.
 
-In another aspect, the air above flow, so that evaporation heat of water increases.
+The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.
 
@@
 \label{sec:effects of bubble bath additive}
+When bubble bath additive is added while initially filling the bathtub, bubble stay on the surface and restraint the evaporation of water to air. So water losses less heat.
+
+The effect is that less heat is called for to keep the temperature. So $u_h$ decreases for best strategy to keep the temperature.
 

### 2016-02-01 Tex/paper.tex
correction 2.0 added

--- 2016-02-01 Tex/paper.tex
@@
 \begin{itemize}
-\item We change the shape of the bathtub to sphere and elliptical with the same strategy.
-The temperature graphic shows that sphere is the most proper shape for keeping water temperature.
-Square performs the worst on keeping temperature.
-However, temperature of square bathtub is more evenly than others.
+\item We change the shape of the bathtub to sphere and cylinder with the same strategy.
+The temperature graph shows that sphere is the properest shape for keeping water temperature.
+The cylinder is proved to be the worst on keeping temperature.
+However, temperature of cylinder bathtub is evener than others.
 \item We change the volume of the bathtub without changing the proportion.
-The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increased as volume increases.
+The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
 \end{itemize}
@@
 \label{sec:effects of motion}
-When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases. That means heat exchange between water and person increases.
+When the person in the bathtub makes motions, the heat exchange coefficient between the person and water ${\gamma}_2$ increases.
+That means heat exchange between water and the person increases.
+In another aspect, the air above flows, so that evaporation heat of water increases.
+Water loses more heat.
 
-In another aspect, the air above flow, so that evaporation heat of water increases.
+The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.
 
@@
 \label{sec:effects of bubble bath additive}
+When bubble bath additive is added while initially filling the bathtub, bubbles stay on the surface and the evaporation of water to air is limitted. So water loses less heat.
+
+The effect is that less heat is needed to keep the temperature. So $u_h$ for best strategy decreases to keep the temperature.
 
@@
 \item Our model build a 3D geometry to simulate the research object so
-\item The network we built include both microcosmic part and
+\item The network we built includes both microcosmic part and
   macrocosmic part, and they react to each other.

### 2016-02-01 Tex/paper.tex
constant and variable added

@@
   $V$            &Total volume of water \\
+  $v$            &Speed of air\\
   $x_s$          &Humidity ratio in saturated air \\
+  $x$            &Humidity ratio in the air \\
   $x_0$          &Initial humidity ratio in the air \\
@@
   $u_2$          &Temperature of person's surface \\
+  $g$            &???\\
+\end{tabular}
+\end{table}
 
+\textbf{Table 2}.
+\begin{table}
+\begin{tabular}{l|l}
   Variable & Description \\
@@
   $u_3$          &Temperature of bathtub \\
+  $u_h$          &Temperature of hot water from faucet \\
 \end{tabular}

### 2016-02-01 Tex/paper.tex
reference added

@@
 
-\bibitem{}
+\bibitem{1} http://www.engineeringtoolbox.com
+
+\bibitem{2} Umesh Gaur, Suk-fai Lau, Brent B.
+Wunderlich, and Bernhard Wunderlich, Heat Capacity and Other Thermodynamic Properties of Linear Macromolecules VI.
+Acrylic Polymers, J.Phys.Chem.Ref.Data, Vol.11, No4, 1982.
+
+\bibitem{3} https://www.professionalplastics.com/professionalplastics/content/castacrylic.pdf
+
+\bibitem{4} A.
+Khabari, M.
+Zenouzi, T.
+O’Connor and A.
+Rodas, Natural and Forced Convective Heat Transfer Analysis of Nanostructured Surface, Proceedings of the World Congress on Engineering 2014 Vol I, WCE 2014, July 2 - 4, 2014, London, U.K.
+
+\bibitem{5} http://www.nzifst.org.nz/unitoperations/httrtheory3.htm
+
+\bibitem{6} http://www.engineersedge.com/heat\_transfer/convective\_heat\_transfer\_coefficients\_\_13378.htm
+
+\bibitem{7} de Dear.
+Richard J., Arens.
+Edward A, Zhang Hui and Oguro.
+Masayuki, Convective and radiative heat transfer coefficients for individual human body segments, Int J Biometeorol (1997) 40:141–156
+
+\bibitem{8} http://www.hcheattransfer.com/coefficients.html
 

### 2016-02-01 Tex/paper.tex
tt

--- 2016-02-01 Tex/paper.tex
@@
 
-In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, and they are time-dependant functions. It takes several steps to calculate them.
+In the equation above, $u_3$ is temperature of bathtub, we assume it is unchangeable and as same as initial air temperature.
+
+While $u_1$ i, the temperature of air, is time-dependant, because water vapor transfer heat to air.
+We can calculate $u_1$ by calculating the energy of water vapor evaporated in the air.
+Referencing the deduction of evaporation in the last section,
+\begin{equation}
+  u_1=u_0+\frac{{C_w}\rho}{{C_a}{{\rho}_a}(x_s-x_0)(1-e^{-\lambda t})
+\end{equation}
 
@@
 \end{center}
+In each operation, $u_2$ is taken as $33.5^{\circ}\mathrm$ and the initial value condition is $u=35^{\circ}\mathrm$. Then the result performs like this []
+
+Comparing the temperature distribution of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.
 
@@
 \begin{itemize}
-\item We change the shape of the bathtub to sphere and cylinder with the same strategy.
-The temperature graph shows that sphere is the properest shape for keeping water temperature.
-The cylinder is proved to be the worst on keeping temperature.
-However, temperature of cylinder bathtub is evener than others.
+\item We change the shape of the bathtub to sphere and elliptical with the same strategy.
+The temperature graphic shows that sphere is the most proper shape for keeping water temperature.
+Square performs the worst on keeping temperature.
+However, temperature of square bathtub is more evenly than others.
 \item We change the volume of the bathtub without changing the proportion.
-The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
+The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increased as volume increases.
 \end{itemize}
@@
 \begin{itemize}
-\item
-\item
-\item
+\item Comparing the temperature graph with different shape of the person, we found when the shape gets more regular, $u_h$, $v_h$ becomes decreases relatively.
+\item The larger the person, the more heat between water and the person. That means more heat is called for. $u_h$, $v_h$ for best strategy increases.
+\item When the surface temperature of the person increases, it becomes more closed to water temperature.
+Then water and person have less heat exchange.
+Less heat of hot water from faucet is called for.
+$u_h$, $v_h$ for best strategy decreases.
 \end{itemize}
@@
 \label{sec:effects of motion}
-When the person in the bathtub makes motions, the heat exchange coefficient between the person and water ${\gamma}_2$ increases.
-That means heat exchange between water and the person increases.
-In another aspect, the air above flows, so that evaporation heat of water increases.
-Water loses more heat.
+When the person in the bathtub make motions, the heat exchange coefficient between person and water ${\gamma}_2$ increases.
+That means heat exchange between water and person increases.
+In another aspect, the air above flow, so that evaporation heat of water increases.
+Water losses more heat.
 
-The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.
+The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.
 
@@
 \label{sec:effects of bubble bath additive}
-When bubble bath additive is added while initially filling the bathtub, bubbles stay on the surface and the evaporation of water to air is limitted. So water loses less heat.
+When bubble bath additive is added while initially filling the bathtub, bubble stay on the surface and restraint the evaporation of water to air. So water losses less heat.
 
-The effect is that less heat is needed to keep the temperature. So $u_h$ for best strategy decreases to keep the temperature.
+The effect is that less heat is called for to keep the temperature. So $u_h$ decreases for best strategy to keep the temperature.
 
@@
 \item Our model build a 3D geometry to simulate the research object so
-\item The network we built includes both microcosmic part and
+\item The network we built include both microcosmic part and
   macrocosmic part, and they react to each other.

### 2016-02-01 Tex/paper.tex
12

--- 2016-02-01 Tex/paper.tex
@@
 \label{sec:introduction}
-\begin{displaymath}
-Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
-\end{displaymath}
-
-\begin{displaymath}
-\begin{aligned}
-\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
-& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
-& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
-\end{aligned}
-\end{displaymath}
-
-\begin{displaymath}
-\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
-\end{displaymath}
-
-\begin{displaymath}
-Q=\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz
-\end{displaymath}
-
-\begin{displaymath}
-\begin{aligned}
-\int_{t_1}^{t_2} \iint\limits_{\Gamma}k\frac{\partial u}{\partial n}dsdt & =\iiint\limits_{\Omega}\rho C_{w}(u_f - u_i)dx dy dz\\
-& =\int_{t_1}^{t_2}\iiint\limits_{\Omega}[\frac{\partial}{\partial x}(k\frac{\partial u}{\partial x})+\frac{\partial}{\partial y}(k\frac{\partial u}{\partial y})+\frac{\partial}{\partial z}(k\frac{\partial u}{\partial z})]dxdydx\\
-& = \iiint\limits_{\Omega}\rho C_{w}(\int_{t_1}^{t_2}\frac{\partial u}{\partial t}dt)dxdydz
-\end{aligned}
-\end{displaymath}
-
-\begin{displaymath}
-\rho C_{w}\frac{\partial u}{\partial t}=k\bigtriangleup u+\frac{C_w V_h(u_h-u)}{V}-\frac{C_v g}{V}
-\end{displaymath}
 
@@
 In the third step, we develop the conclusion of the strategy.
+
+\section{Terminology}
+\label{sec:terminology}
+
+Definitions of symbols employed in this paper are listed in
+\textbf{Table 1}.
+\begin{table}
+\begin{tabular}{l|l}
+  Constant & Description \\
+  \hline
+  $k$            &Thermal conductivity of water \\
+  $\rho$         &Density of water \\
+  ${\rho}_a$     &Density of air \\
+  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
+  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
+  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
+  $C_w$          &Specific heat capacity of water \\
+  $C_a$          &Specific heat capacity of air \\
+  $V$            &Total volume of water \\
+  $V_a$          &Total volume of air above the water \\
+  $v$            &Flow velocity of air\\
+  $x_s$          &Humidity ratio in saturated air \\
+  $x$            &Humidity ratio in the air \\
+  $x_0$          &Initial humidity ratio in the air \\
+  $A$            &Square of water surface \\
+  $V_a$          &Volume of surrounding air \\
+  $C_v$          &Evaporation heat of water \\
+\end{tabular}
+\end{table}
+
+\textbf{Table 2}.
+\begin{table}
+\begin{tabular}{l|l}
+  Variable & Description \\
+  \hline
+  $t$            &time \\
+  $u$            &Temperature of water \\
+  $u$            &Temperature of water when t=0 \\
+  $u_1$          &Temperature of air \\
+  $u_2$          &Temperature of person's surface \\
+  $u_3$          &Temperature of bathtub \\
+  $u_h$          &Temperature of hot water from faucet \\
+  $v_h$          &Velocity of hot water from faucet \\
+  $g$            &Evaporation heat of water\\
+\end{tabular}
+\end{table}
 
@@
 \label{sec:human-capital-model}
-Definitions of symbols employed in this paper are listed in
-\textbf{Table 1}.
-\begin{table}
-\begin{tabular}{l|l}
-  Constant & Description \\
-  \hline
-  $k$            &Thermal conductivity of water \\
-  $\rho$         &Density of water \\
-  ${\gamma}_1$   &Heat exchange coefficient between water and air \\
-  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
-  ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
-  $C_w$          &Specific heat capacity of water \\
-  $V$            &Total volume of water \\
-  $v$            &Speed of air\\
-  $x_s$          &Humidity ratio in saturated air \\
-  $x$            &Humidity ratio in the air \\
-  $x_0$          &Initial humidity ratio in the air \\
-  $A$            &Square of water surface \\
-  $V_a$          &Volume of surrounding air \\
-  $C_v$          &Evaporation heat of water \\
-  $u_2$          &Temperature of person's surface \\
-  $g$            &???\\
-\end{tabular}
-\end{table}
-
-\textbf{Table 2}.
-\begin{table}
-\begin{tabular}{l|l}
-  Variable & Description \\
-  \hline
-  $u$            &Temperature of water \\
-  $u_1$          &Temperature of air \\
-  $u_3$          &Temperature of bathtub \\
-  $u_h$          &Temperature of hot water from faucet \\
-\end{tabular}
-\end{table}
 
@@
 
-In this part, we use physical theorem to deduce the heat conduction equation
-in the bathtub.
+In this part, we use physical theorem to deduce the heat conduction equation in the bathtub.
 
 Figure 1 shows thermal analysis of water in bathtub.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{2.pdf}\\
+  \caption{Thermal Analysis of Water}\label{1_p}
+\end{figure}
 
 First, we assume that the heat change of all the water in a tiny time $\Delta t$ from $t_1$ to $t_2$ is $\Delta Q$.
-As it shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
+As shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
 In addition, heat changes when the hot water flow in and the excess water flow out.
@@
 \end{equation}
-, in which $\Omega$ is the region of water, $\rho$ represents the density of water, $u_f$ stands for the final temperature when t=$t_2$, and $u_i$ is the initial temperature when t=$t_1$.
+in which $\Omega$ is the region of water, $\rho$ represents the density of water, $u_f$ stands for the final temperature when t=$t_2$, and $u_i$ is the initial temperature when t=$t_1$.
 
@@
 \end{equation}
-holds for the heat flow through surface with square of dS, as it shown in Figure 2.
+holds for the heat flow through surface with square of dS, as it shows in Figure 2.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{1.pdf}\\
+  \caption{Thermal Analysis}\label{2_p}
+\end{figure}
 In the equation, k is thermal conductivity, $\frac{\partial u}{\partial n}$ is the derivative of u along the normal line. Thus, after integration of dQ by time and space
@@
 in which $x_0$ is the initial humidity ratio in the air, $\rho$ is the density of water, $V_a$ is the total volume of surrounding air.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{3.pdf}\\
+  \caption{Evaporation}\label{3_p}
+\end{figure}
 
@@
 
-In the equation above, $u_1$, $u_3$ are temperatures of air and bathtub, and they are time-dependant functions. It takes several steps to calculate them.
+In the equation above, $u_3$ is temperature of bathtub, we assume it is unchangeable and as same as initial air temperature.
+
+While $u_1$ i, the temperature of air, is time-dependant, because water vapor transfer heat to air.
+We can calculate $u_1$ by calculating the energy of water vapor evaporated in the air.
+Referencing the deduction of evaporation in the last section,
+\begin{equation}
+  u_1=u_0+\frac{C_w\rho}{C_a{{\rho}_a}} (x_s-x_0)(1-e^{-\lambda t})
+\end{equation}
 
@@
 
-First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure 2. Matlab divided the geometry into several elements.
+First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure 4. Matlab divided the geometry into several elements.
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{4.png}\\
+  \caption{3D geometry of water}\label{4_p}
+\end{figure}
 
@@
 \begin{center}
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{c|c}
 \hline
-      &$v_h$  &$u_h$        \\ \hline
- 1    &0.1             & 50              \\ \hline
- 2    &0.2             & 50              \\ \hline
- 3    &0.3             & 50              \\ \hline
- 4    &0.1             & 40              \\ \hline
- 5    &0.2             & 40              \\ \hline
- 6    &0.3             & 40              \\ \hline
- 7    &0.1             & 30              \\ \hline
- 8    &0.2             & 30              \\ \hline
- 9    &0.3             & 30              \\ \hline
+    $v_h kg/s$  &${u_h}\,^{\circ}\mathrm{C}$        \\ \hline
+     0.1             & 50              \\ \hline
+    0.2             & 50              \\ \hline
+     0.3             & 50              \\ \hline
+     0.1             & 40              \\ \hline
+     0.2             & 40              \\ \hline
+     0.3             & 40              \\ \hline
+     0.1             & 30              \\ \hline
+     0.2             & 30              \\ \hline
+     0.3             & 30              \\ \hline
 \end{tabular}
 \end{center}
+In each operation, $u_2$ is taken as $33.5\,^{\circ}\mathrm{C}$
+and the initial value condition is $35\,^{\circ}\mathrm{C}$.
+ We take 120s as time period. Then the result performs like the following graphs show.
+
+Figure 5, Figure 6, Figure 7 shows the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{6-2.pdf}\\
+  \caption{$u_h=40$,$v_h=0.1$,t=240}\label{6-2_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{10-2.pdf}\\
+  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{11-2.pdf}\\
+  \caption{$u_h=40$,$v_h=0.3$,t=240}\label{11-2_p}
+\end{figure}
+
+Figure 8, Figure 9, Figure 10 show the temperature at t=600
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{6-5.pdf}\\
+  \caption{$u_h=40$,$v_h=0.1$,t=600}\label{6-5_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{10-5.pdf}\\
+  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-5_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{11-5.pdf}\\
+  \caption{$u_h=40$,$v_h=0.3$,t=600}\label{11-5_p}
+\end{figure}
+
+It indicates that keep $u_h$, temperature increases when $v_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
+
+Figure 11, Figure 12, Figure 13 show the temperature of water at t=240, with $v_h=0.2$ and $u_h=30, 40 and 50$
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{8-2.pdf}\\
+  \caption{$u_h=30$,$v_h=0.2$,t=240}\label{8-2_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{10-2.pdf}\\
+  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{4-2.pdf}\\
+  \caption{$u_h=50$,$v_h=0.2$,t=240}\label{4-2_p}
+\end{figure}
+
+Figure 14, Figure 15, Figure 16 show the temperature at t=600
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{8-5.pdf}\\
+  \caption{$u_h=30$,$v_h=0.2$,t=600}\label{8-5_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{10-5.pdf}\\
+  \caption{$u_h=40$,$v_h=0.2$,t=600}\label{10-5_p}
+\end{figure}
+
+\begin{figure}[htb]
+  \centering
+  \includegraphics[width=8cm]{4-5.pdf}\\
+  \caption{$u_h=50$,$v_h=0.2$,t=600}\label{4-5_p}
+\end{figure}
+
+It indicates that keep $v_h$, temperature increases when $u_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
+
+Comparing the temperature distribution of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.
 
@@
 \begin{itemize}
-\item We change the shape of the bathtub to sphere and cylinder with the same strategy.
-The temperature graph shows that sphere is the properest shape for keeping water temperature.
-The cylinder is proved to be the worst on keeping temperature.
-However, temperature of cylinder bathtub is evener than others.
+\item We change the shape of the bathtub to sphere and cylinder to get the best strategy. The result shows that the bathtub with the shape of sphere is the most effective in keeping temperature.
+\begin{center}
+\begin{tabular}{c|c|c}
+\hline
+ Shape     &$v_h$  &$u_h$        \\ \hline
+ Square    &0.2             & 40              \\ \hline
+ Sphere    &0.15            & 40              \\ \hline
+ Cylinder  &0.2             & 45              \\ \hline
+\end{tabular}
+\end{center}
      \item We change the volume of the bathtub without changing the proportion.
-The result as following Table [] shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
+The result in the following table shows that with the same $v_h$, $u_h$ increases as volume increases; with the same $u_h$, $v_h$ increases as volume increases.
 \end{itemize}
@@
 \begin{itemize}
-\item
-\item
-\item
+\item Comparing the temperature graph with different shape of the person, we found when the shape gets more regular, $u_h$, $v_h$ decreases relatively.
+\item Change the volume of the person. The result shows that, $u_h$, $v_h$ for best strategy increases when the volume increases.
+\item Change the surface temperature of the person to get the best strategy. The result shows no noticeable change.
+    \begin{center}
+\begin{tabular}{c|c|c}
+\hline
+ Surface Temperature     &$v_h$  &$u_h$        \\ \hline
+ $u_2=33.5$    &0.2             & 40              \\ \hline
+ $u_2=33.5$    &0.15            & 40              \\ \hline
+ $u_2=33.5$  &0.2             & 45              \\ \hline
+\end{tabular}
+\end{center}
 \end{itemize}
@@
 
+The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.
+
 The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.
@@
 \label{sec:effects of bubble bath additive}
-When bubble bath additive is added while initially filling the bathtub, bubbles stay on the surface and the evaporation of water to air is limitted. So water loses less heat.
+When bubble bath additive is added while initially filling the bathtub, bubbles stay on the surface and the evaporation of water to air is limited. So water loses less heat.
 
@@
 \item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
-\item Our model build a 3D geometry to simulate the research object so
-\item The network we built includes both microcosmic part and
-  macrocosmic part, and they react to each other.
+\item Our model build a 3D geometry to simulate the research object so it can show the exact situation.
+\item Our model operates with different strategies and display the result by 3D geometry graph, so they could be compared in a visible way.
 \item Our model proves the effect of time.
@@
 Water-in in high temperature loses it's energy quickly, and water-in in low temperature is unable to warm your surrounding.
-It's best that you set the speed of the water-in at xxx, and temperature at yyy.
+It's best that you set the speed of the water-in at 0.2kg/s, and temperature at $40\,^{\circ}\mathrm{C}$.
 \item Further more, your movement effects the water.

### 2016-02-01 Tex/paper.tex

@@
 \begin{itemize}
-\item Obviously, the water exchange thermal energy directly with the air. That's why you can see water vapour float above the water.
+\item Obviously, the water exchange thermal energy directly with the air.
+That's why you can see water vapour float above the water.
+The temperature of water decreases as a result of the heat exchange.
 \item On the other hand, the bathtub is cooler than the water on most occasions.
@@
 However, the bathtub conduct heat easily, while in this way the air's temperature rises.
+In other words, the temperature of water decreases faster.
 \end{itemize}
-From statement above, you may understand our bathtub can't stay in a even temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more in your bath :
+From statement above, you may understand our bathtub can't stay in an even temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more during your bath :
 \begin{itemize}
@@
 \end{itemize}
+We hope you enjoy your bath.
 

### 2016-02-01 Tex/paper.tex
fix typo

@@
 \begin{itemize}
-\item Build a basic model that demonstrate the change of the temperature in the bathtub in space and time without other intervention.
+\item Build a basic model that demonstrates the change of the temperature in the bathtub in space and time without other interventions.
 \item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
@@
 The shape of the bathtub is a cuboid, and the person will stay still.
-In the second step, the person move slowly and the shape of the bathtub changes.
+In the second step, the person moves slowly and the shape of the bathtub changes.
 In the third step, we develop the conclusion of the strategy.
@@
 Definitions of symbols employed in this paper are listed in
-\textbf{Table 1}.
+\textbf{Table \ref{1_t}}.
 \begin{table}
@@
 \end{tabular}
+\caption{Constant}\label{1_t}
 \end{table}
 
-\textbf{Table 2}.
+\textbf{Table \ref{2_t}}.
 \begin{table}
@@
 \end{tabular}
+\caption{Variable}\label{2_t}
 \end{table}
@@
 of water temperature in the bathtub. The initial-boundary value conditions are deduced according to
-Fourier theorem, vaporization equation[ ].
+Fourier theorem, vaporization equation\cite{1}.
 
@@
 As shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
-In addition, heat changes when the hot water flow in and the excess water flow out.
+In addition, heat changes when the hot water flows in and the excess water flows out.
 Thus $\Delta Q$ is divided into five parts, i.e.
@@
 $\Delta Q_2$ is the heat of the hot water from the faucet in $\Delta t$,
-$\Delta Q_3$ is the heat of the water flow away in $\Delta t$,
+$\Delta Q_3$ is the heat of the water flows away in $\Delta t$,
 $\Delta Q_4$ is the heat loss because of vaporization.
@@
 
-Considering the right side of equation 1.
+Considering the right side of equation 1,
  Fourier theorem indicates that,
@@
 \end{equation}
-holds for the heat flow through surface with square of dS, as it shows in Figure 2.
+holds for the heat flows through surface with square of dS, as it shows in Figure 2.
 \begin{figure}[htb]
@@
 in which $\Gamma$ is the boundary of $\Omega$,
-the heat flow into the water by thermal conduction could be calculated.
+the heat flows into the water by thermal conduction could be calculated.
 

### 2016-02-01 Tex/paper.tex
fix typo

@@
 
-Definitions of symbols employed in this paper are listed in
-\textbf{Table \ref{1_t}}.
+Definitions of symbols employed in this paper are listed in Table \ref{1_t} and Table \ref{2_t}.
 \begin{table}
@@
 
-\textbf{Table \ref{2_t}}.
 \begin{table}
@@
 
-Figure 1 shows thermal analysis of water in bathtub.
+Figure \ref{1_p} shows thermal analysis of water in bathtub.
 \begin{figure}[htb]
@@
 \end{equation}
-holds for the heat flows through surface with square of dS, as it shows in Figure 2.
+holds for the heat flows through surface with square of dS, as it shows in Figure \ref{2_p}.
 \begin{figure}[htb]
@@
 Now let's discuss g, evaporation rate per square.
-As Figure 3 shows, water evaporates into air and air humidity increases, until it is saturate. According to empirical formula in [], we know that
+As Figure \ref{3_p} shows, water evaporates into air and air humidity increases, until it is saturate. According to empirical formula\cite{1}, we know that
 \begin{equation}
@@
 
-Boundary value conditions are quite essential in partial differential equations. In our model, water is not a regular research object.
-Thus boundary value condition is complex.
+Boundary value conditions are quite essential in partial differential equations. In our model, water is not a regular object. Thus boundary value condition is complex.
 
@@
 
-Since person is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
+Since bather is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
 as the Dirichlet value condition. That is
@@
 \end{equation}
-In the equation, i=1 or 3 and $u_i$ is the temperature of contact material,
+In the equation, i=1 or 3 ,$u_i$ is the temperature of contact material, and 
 ${\gamma}_i$ is the heat exchange coefficient of ${\Gamma}_i$.
@@
 
-While $u_1$ i, the temperature of air, is time-dependant, because water vapor transfer heat to air.
-We can calculate $u_1$ by calculating the energy of water vapor evaporated in the air.
+$u_1$, the temperature of air, is time-dependant, because water vapor transfer heat to air.
+We can calculate $u_1$ by calculating the energy of water vapor evaporating in the air.
 Referencing the deduction of evaporation in the last section,
@@
 \label{sec:PDE solution}
-Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this kind of problem.
+Since our equations are complex and the region is quite irregular, it's impossible to get a analytical solution. Finite element method is normally adopted to deal with this kind of problem.
 
 We use Partial Differential Equation Toolbox in matlab to solve our equations.
-Partial Differential Equation Toolbox makes use of finite element method to separate irregular geometry and calculate a relatively precise solution, get solution of temperature corresponding to different $u_h$ and $v_h$.
-By comparing temperature distribution, we choose proper parameters as the best strategy.
+Partial Differential Equation Toolbox makes use of finite element method to separate irregular geometry, calculate a relatively precise solution, and get solution of temperature corresponding to different $u_h$ and $v_h$.
+By comparing temperature distributions, we choose proper parameters as the best strategy.
 
-First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure 4. Matlab divided the geometry into several elements.
+First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure \ref{4_p}. Matlab divides the geometry into several elements.
 \begin{figure}[htb]
@@
 
-Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
+Our strategy focus on two variables, $v_h$ and $u_h$. We test about fifty pairs of data to find the best strategy. And we list nine representative pairs of data in Table \ref{3_t}.
+
+\begin{table}
 \begin{center}
@@
 \end{center}
+\caption{Represenative Data Pairs}\label{3_t}
+\end{table}
+
 In each operation, $u_2$ is taken as $33.5\,^{\circ}\mathrm{C}$
 and the initial value condition is $35\,^{\circ}\mathrm{C}$.
- We take 120s as time period. Then the result performs like the following graphs show.
+ We take 120s as time period. The following graphs show the results we get.
 
-Figure 5, Figure 6, Figure 7 shows the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
+Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
 \begin{figure}[htb]
@@
   \includegraphics[width=8cm]{6-2.pdf}\\
-  \caption{$u_h=40$,$v_h=0.1$,t=240}\label{6-2_p}
+  \caption{$u_h=40$, $v_h=0.1$, t=240}\label{5_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{10-2.pdf}\\
-  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
+  \caption{$u_h=40$, $v_h=0.2$, t=240}\label{6_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{11-2.pdf}\\
-  \caption{$u_h=40$,$v_h=0.3$,t=240}\label{11-2_p}
+  \caption{$u_h=40$,$v_h=0.3$,t=240}\label{7_p}
 \end{figure}

### 2016-02-01 Tex/paper.tex
123

--- 2016-02-01 Tex/paper.tex
@@
 \begin{itemize}
-\item \textbf{assumption 1} If an employee has probability to
-  promote, he won't churn.
+\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.
 
-The possibility of the unforeseen accidents, which could force an
-employee to leave his position,is neglected.Human nature, an employee
-will stay at his position to chase for higher level.
+    Since human-being is temperature-constant, and bathtub contacts the ground, we can assume that they have no heat exchange.
 
-\item \textbf{assumption 2} For a vacancy,if there exists an
-  employee measures up to it already,ICM won't recruit for it.
+\item \textbf{assumption 2} The volume of water flowing away is equivalent to that of hot water at any time.
 
-Since recruiting good people is difficult, time consuming and
-expensive according to issue 5,it is wasteful to recruit for a
-position if an employee can promote to it.
+    Although water has evaporation loss and other kinds of losses,  it takes up a small proportion of the total volume. Thus we sensibly neglect them.
 
-\item \textbf{assumption 3} Demotion won't occur.
+\item \textbf{assumption 3} The hot water from the faucet has a constant flow velocity and temperature.
 
-\item \textbf{assumption 4} Administrative clerk won't promote or be
-  transferred.
+\item \textbf{assumption 4} There is no convection in the water.
+
+The temperature water in the bathtub is a relatively
 

### 2016-02-01 Tex/paper.tex
123

@@
 
-The temperature water in the bathtub is a relatively
+Since the temperature of water in the bathtub is relatively uniform, the slight convection won't influence heat exchange.
 
-\item \textbf{assumption 5} For the promotion probability and
-  organization change, the other factors effects the churn probability
-  is invariable.
-
-Though churn derives from varieties of reasons and they are actually
-lacking of known conditions and data to estimate them, we have to
-regard it as stable in our model.
-
-\item \textbf{assumption 6} Each division or office have at least one
-  middle manager or senior manager.
-
+\item \textbf{assumption 5} Water, bathtub, person and the surrounding air compose a closed heat system.
 \end{itemize}

### 2016-02-01 Tex/paper.tex
fix typo

--- 2016-02-01 Tex/paper.tex
@@
 \begin{itemize}
-\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.
+\item \textbf{assumption 1} If an employee has probability to
+  promote, he won't churn.
 
-    Since human-being is temperature-constant, and bathtub contacts the ground, we can assume that they have no heat exchange.
+The possibility of the unforeseen accidents, which could force an
+employee to leave his position,is neglected.Human nature, an employee
+will stay at his position to chase for higher level.
 
-\item \textbf{assumption 2} The volume of water flowing away is equivalent to that of hot water at any time.
+\item \textbf{assumption 2} For a vacancy,if there exists an
+  employee measures up to it already,ICM won't recruit for it.
 
-    Although water has evaporation loss and other kinds of losses,  it takes up a small proportion of the total volume. Thus we sensibly neglect them.
+Since recruiting good people is difficult, time consuming and
+expensive according to issue 5,it is wasteful to recruit for a
+position if an employee can promote to it.
 
-\item \textbf{assumption 3} The hot water from the faucet has a constant flow velocity and temperature.
+\item \textbf{assumption 3} Demotion won't occur.
 
-\item \textbf{assumption 4} There is no convection in the water.
-
-The temperature water in the bathtub is a relatively
+\item \textbf{assumption 4} Administrative clerk won't promote or be
+  transferred.
 
@@
 
-Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
 \begin{figure}[htb]
@@
 
-Figure 8, Figure 9, Figure 10 show the temperature at t=600
+Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
+
 \begin{figure}[htb]
@@
   \includegraphics[width=8cm]{6-5.pdf}\\
-  \caption{$u_h=40$,$v_h=0.1$,t=600}\label{6-5_p}
+  \caption{$u_h=40$,$v_h=0.1$,t=600}\label{8_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{10-5.pdf}\\
-  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-5_p}
+  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{9_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{11-5.pdf}\\
-  \caption{$u_h=40$,$v_h=0.3$,t=600}\label{11-5_p}
+  \caption{$u_h=40$,$v_h=0.3$,t=600}\label{10_p}
 \end{figure}
 
-It indicates that keep $u_h$, temperature increases when $v_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
+Figure \ref{8_p}, Figure \ref{9_p}, Figure \ref{10_p} show the temperature at t=600
 
-Figure 11, Figure 12, Figure 13 show the temperature of water at t=240, with $v_h=0.2$ and $u_h=30, 40 and 50$
+It indicates that when $u_h$ is constant, temperature increases when $v_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
 
@@
   \includegraphics[width=8cm]{8-2.pdf}\\
-  \caption{$u_h=30$,$v_h=0.2$,t=240}\label{8-2_p}
-\end{figure}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=8cm]{10-2.pdf}\\
-  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
+  \caption{$u_h=30$,$v_h=0.2$,t=240}\label{11_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{4-2.pdf}\\
-  \caption{$u_h=50$,$v_h=0.2$,t=240}\label{4-2_p}
+  \caption{$u_h=50$,$v_h=0.2$,t=240}\label{12_p}
 \end{figure}
 
-Figure 14, Figure 15, Figure 16 show the temperature at t=600
+Figure \ref{11_p}, Figure \ref{6_p}, Figure \ref{12_p} show the temperature of water at t=240, with $v_h=0.2$ and $u_h=30, 40 and 50$
 
@@
   \includegraphics[width=8cm]{8-5.pdf}\\
-  \caption{$u_h=30$,$v_h=0.2$,t=600}\label{8-5_p}
-\end{figure}
-
-\begin{figure}[htb]
-  \centering
-  \includegraphics[width=8cm]{10-5.pdf}\\
-  \caption{$u_h=40$,$v_h=0.2$,t=600}\label{10-5_p}
+  \caption{$u_h=30$,$v_h=0.2$,t=600}\label{13_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{4-5.pdf}\\
-  \caption{$u_h=50$,$v_h=0.2$,t=600}\label{4-5_p}
+  \caption{$u_h=50$,$v_h=0.2$,t=600}\label{14_p}
 \end{figure}
 
-It indicates that keep $v_h$, temperature increases when $u_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
+Figure \ref{13_p}, Figure \ref{9_p}, Figure \ref{14_p} show the temperature at t=600
 
-Comparing the temperature distribution of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.
+It indicates that when $v_h$ is constant, temperature increases when $u_h$ increases, and the system becomes more stable as time goes on. It proves that our model is sensible.
+
+Comparing the temperature distributions of each strategy, with least water waste, we choose $v_h=0.2$, $u_h=40$ as the best strategy to keep the temperature.
 
@@
 \label{sec:parameters of bathtub}
-\begin{itemize}
-\item We change the shape of the bathtub to sphere and cylinder to get the best strategy. The result shows that the bathtub with the shape of sphere is the most effective in keeping temperature.
+
+\begin{table}
 \begin{center}
@@
 \end{center}
+\caption{Shape of Bathtub}\label{4_t}
+\end{table}
+
+\begin{itemize}
+
+\item We change the shape of the bathtub to sphere and cylinder to get the best strategy.
+The result shown in Table \ref{4_t} that the bathtub with the shape of sphere is the most effective in keeping temperature.
+
      \item We change the volume of the bathtub without changing the proportion.
@@
 \begin{itemize}
-\item Comparing the temperature graph with different shape of the person, we found when the shape gets more regular, $u_h$, $v_h$ decreases relatively.
-\item Change the volume of the person. The result shows that, $u_h$, $v_h$ for best strategy increases when the volume increases.
-\item Change the surface temperature of the person to get the best strategy. The result shows no noticeable change.
+\item Comparing the temperature graphs with different shapes of the bather, we find when the shape gets more regular, $u_h$, $v_h$ decreases relatively.
+\item Change the volume of the bather. The result shows that, $u_h$, $v_h$ for best strategy increases when the volume increases.
+\item Change the surface temperature of the bather to get the best strategy. The result shows no noticeable change.
+\begin{table}
 \begin{center}
@@
 \end{center}
+\caption{Surface Temperature}\label{5_t}
+\end{table}
 \end{itemize}
@@
 \label{sec:effects of motion}
-When the person in the bathtub makes motions, the heat exchange coefficient between the person and water ${\gamma}_2$ increases.
-That means heat exchange between water and the person increases.
+When the bather in the bathtub makes motions, the heat exchange coefficient between the bather and water ${\gamma}_2$ increases.
+That means heat exchange between water and the bather increases.
 In another aspect, the air above flows, so that evaporation heat of water increases.
@@
 The effect is that more heat is called for to keep the temperature. So $u_h$ increases for best strategy to keep the temperature.
-
-The effect is that more heat is needed to keep the temperature, consequently $u_h$ as the best strategy increases to keep the temperature.
 
@@
 \begin{itemize}
-\item Our model make good use of thermology knowledge so it can reflect the situation in the real world realistically.
-\item Our model build a 3D geometry to simulate the research object so it can show the exact situation.
-\item Our model operates with different strategies and display the result by 3D geometry graph, so they could be compared in a visible way.
+\item Our model makes good use of thermology knowledge so it can reflect the situation in the real world realistically.
+\item Our model builds a 3D geometry to simulate the research object so it can show the exact situation.
+\item Our model operates with different strategies and displays the result by 3D geometry graph, so they could be compared in a visible way.
 \item Our model proves the effect of time.
@@
 \begin{itemize}
-\item We assume that the water is still. In fact, streams flow and fluid dynamic is better taken into consideration. The actual situation is much complicated.
-\item The model of the person should be more realistic. In fact, model of human body includes hands, legs or other parts, and the surface of human skin isn't even.
-\item The condensation of water should be taken into consideration. Water that evaporate become water vapour, and some will condense into water on the bathtub.
+\item We assume that the water is still. In fact, it is better to take the streams flow and fluid dynamic into consideration. The actual situation is much more complicated.
+\item The model of the bather should be more realistic. In fact, model of human body includes hands, legs or other parts, and the surface of human skin isn't even.
+\item The condensation of water should be taken into consideration. Water that evaporates become water vapour, and some will condense into water on the bathtub.
 \end{itemize}
@@
 \begin{itemize}
-\item Obviously, the water exchange thermal energy directly with the air.
-That's why you can see water vapour float above the water.
+\item Obviously, the water exchanges thermal energy directly with the air.
+That's why you can see water vapour floats above the water.
 The temperature of water decreases as a result of the heat exchange.
-\item On the other hand, the bathtub is cooler than the water on most occasions.
+\item On the other hand, the bathtub is cooler than the water in most occasions.
 It's reasonable that the bathtub absorbs heat from the water.
-However, the bathtub conduct heat easily, while in this way the air's temperature rises.
+However, the bathtub conducts heat easily.
+In this way the air's temperature rises.
 In other words, the temperature of water decreases faster.
 \end{itemize}
-From statement above, you may understand our bathtub can't stay in an even temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more during your bath :
+From statement above, you may understand our bathtub can't stay in an constant temperature evenly. Consequently we have some suggestions for you, if you'd like to enjoy more during your bath :
 \begin{itemize}
@@
 Water-in in high temperature loses it's energy quickly, and water-in in low temperature is unable to warm your surrounding.
-It's best that you set the speed of the water-in at 0.2kg/s, and temperature at $40\,^{\circ}\mathrm{C}$.
+We recommend you set the speed of the water-in at 0.2kg/s, and temperature at $40\,^{\circ}\mathrm{C}$.
 \item Further more, your movement effects the water.

### 2016-02-01 Tex/paper.tex
....

--- 2016-02-01 Tex/paper.tex
@@
 \begin{itemize}
-\item Build a basic model that demonstrates the change of the temperature in the bathtub in space and time without other interventions.
+\item Build a basic model that demonstrate the change of the temperature in the bathtub in space and time without other intervention.
 \item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
@@
 The shape of the bathtub is a cuboid, and the person will stay still.
-In the second step, the person moves slowly and the shape of the bathtub changes.
+In the second step, the person move slowly and the shape of the bathtub changes.
 In the third step, we develop the conclusion of the strategy.
@@
 
-Definitions of symbols employed in this paper are listed in Table \ref{1_t} and Table \ref{2_t}.
+Definitions of symbols employed in this paper are listed in
+\textbf{Table 1}.
 \begin{table}
@@
 \end{tabular}
-\caption{Constant}\label{1_t}
 \end{table}
 
+\textbf{Table 2}.
 \begin{table}
@@
 \end{tabular}
-\caption{Variable}\label{2_t}
 \end{table}
@@
 of water temperature in the bathtub. The initial-boundary value conditions are deduced according to
-Fourier theorem, vaporization equation\cite{1}.
+Fourier theorem, vaporization equation[ ].
 
@@
 
-Figure \ref{1_p} shows thermal analysis of water in bathtub.
+Figure 1 shows thermal analysis of water in bathtub.
+In the photo, $W_1$ is heat exchange between the person and water, while $W_2$ is heat from water vaporization.
+$W_3$ stands for heat exchange between the bathtub and water, and $W_4$ is heat conductivity between water and air.
+$W_5$ represents heat exchange between the bathtub and air, and $W_6$ is heat increasement with hot in-water.
 \begin{figure}[htb]
@@
 As shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
-In addition, heat changes when the hot water flows in and the excess water flows out.
+In addition, heat changes when the hot water flow in and the excess water flow out.
 Thus $\Delta Q$ is divided into five parts, i.e.
@@
 $\Delta Q_2$ is the heat of the hot water from the faucet in $\Delta t$,
-$\Delta Q_3$ is the heat of the water flows away in $\Delta t$,
+$\Delta Q_3$ is the heat of the water flow away in $\Delta t$,
 $\Delta Q_4$ is the heat loss because of vaporization.
@@
 
-Considering the right side of equation 1,
+Considering the right side of equation 1.
 Fourier theorem indicates that,
@@
 \end{equation}
-holds for the heat flows through surface with square of dS, as it shows in Figure \ref{2_p}.
+holds for the heat flow through surface with square of dS, as it shows in Figure 2.
 \begin{figure}[htb]
@@
 in which $\Gamma$ is the boundary of $\Omega$,
-the heat flows into the water by thermal conduction could be calculated.
+the heat flow into the water by thermal conduction could be calculated.
 
@@
 Now let's discuss g, evaporation rate per square.
-As Figure \ref{3_p} shows, water evaporates into air and air humidity increases, until it is saturate. According to empirical formula\cite{1}, we know that
+As Figure 3 shows, water evaporates into air and air humidity increases, until it is saturate. According to empirical formula in [], we know that
 \begin{equation}
@@
 
-Boundary value conditions are quite essential in partial differential equations. In our model, water is not a regular object. Thus boundary value condition is complex.
+Boundary value conditions are quite essential in partial differential equations. In our model, water is not a regular research object.
+Thus boundary value condition is complex.
 
@@
 
-Since bather is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
+Since person is temperature-constant, the boundary value condition of ${\Gamma}_1$ and ${\Gamma}_3$ could be considered
 as the Dirichlet value condition. That is
@@
 \end{equation}
-In the equation, i=1 or 3 ,$u_i$ is the temperature of contact material, and 
+In the equation, i=1 or 3 and $u_i$ is the temperature of contact material,
 ${\gamma}_i$ is the heat exchange coefficient of ${\Gamma}_i$.
@@
 
-$u_1$, the temperature of air, is time-dependant, because water vapor transfer heat to air.
-We can calculate $u_1$ by calculating the energy of water vapor evaporating in the air.
+While $u_1$ i, the temperature of air, is time-dependant, because water vapor transfer heat to air.
+We can calculate $u_1$ by calculating the energy of water vapor evaporated in the air.
 Referencing the deduction of evaporation in the last section,
@@
 \label{sec:PDE solution}
-Since our equations are complex and the region is quite irregular, it's impossible to get a analytical solution. Finite element method is normally adopted to deal with this kind of problem.
+Since our equations are complex and the region is quite irregular, it's impossible to get a regular solution. Finite element method is normally adopted to deal with this kind of problem.
 
 We use Partial Differential Equation Toolbox in matlab to solve our equations.
-Partial Differential Equation Toolbox makes use of finite element method to separate irregular geometry, calculate a relatively precise solution, and get solution of temperature corresponding to different $u_h$ and $v_h$.
-By comparing temperature distributions, we choose proper parameters as the best strategy.
+Partial Differential Equation Toolbox makes use of finite element method to separate irregular geometry and calculate a relatively precise solution, get solution of temperature corresponding to different $u_h$ and $v_h$.
+By comparing temperature distribution, we choose proper parameters as the best strategy.
 
-First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure \ref{4_p}. Matlab divides the geometry into several elements.
+First, we build a 3D geometry model to simulate a proper-size bathtub, as it shown in Figure 4. Matlab divided the geometry into several elements.
 \begin{figure}[htb]
@@
 
-Our strategy focus on two variables, $v_h$ and $u_h$. We test about fifty pairs of data to find the best strategy. And we list nine representative pairs of data in Table \ref{3_t}.
-
-\begin{table}
+Our strategy focus on two variables, $v_h$ and $u_h$. Nine pairs of data are tested to find the best strategy.
 \begin{center}
@@
 \end{center}
-\caption{Represenative Data Pairs}\label{3_t}
-\end{table}
-
 In each operation, $u_2$ is taken as $33.5\,^{\circ}\mathrm{C}$
 and the initial value condition is $35\,^{\circ}\mathrm{C}$.
- We take 120s as time period. The following graphs show the results we get.
+ We take 120s as time period. Then the result performs like the following graphs show.
 
-Figure \ref{5_p}, Figure \ref{6_p}, Figure \ref{7_p} show the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
+Figure 5, Figure 6, Figure 7 shows the temperature of water at t=240, with $u_h=40$ and $v_h=0.1, 0.2 and 0.3$
 \begin{figure}[htb]
@@
   \includegraphics[width=8cm]{6-2.pdf}\\
-  \caption{$u_h=40$, $v_h=0.1$, t=240}\label{5_p}
+  \caption{$u_h=40$,$v_h=0.1$,t=240}\label{6-2_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{10-2.pdf}\\
-  \caption{$u_h=40$, $v_h=0.2$, t=240}\label{6_p}
+  \caption{$u_h=40$,$v_h=0.2$,t=240}\label{10-2_p}
 \end{figure}
@@
   \includegraphics[width=8cm]{11-2.pdf}\\
-  \caption{$u_h=40$,$v_h=0.3$,t=240}\label{7_p}
+  \caption{$u_h=40$,$v_h=0.3$,t=240}\label{11-2_p}
 \end{figure}

### 2016-02-01 Tex/paper.tex

--- 2016-02-01 Tex/paper.tex
@@
 \begin{itemize}
-\item \textbf{assumption 1} If an employee has probability to
-  promote, he won't churn.
+\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.
 
-The possibility of the unforeseen accidents, which could force an
-employee to leave his position,is neglected.Human nature, an employee
-will stay at his position to chase for higher level.
+    Since human-being is temperature-constant, and bathtub contacts the ground, we can assume that they have no heat exchange.
 
-\item \textbf{assumption 2} For a vacancy,if there exists an
-  employee measures up to it already,ICM won't recruit for it.
+\item \textbf{assumption 2} The volume of water flowing away is equivalent to that of hot water at any time.
 
-Since recruiting good people is difficult, time consuming and
-expensive according to issue 5,it is wasteful to recruit for a
-position if an employee can promote to it.
+    Although water has evaporation loss and other kinds of losses,  it takes up a small proportion of the total volume. Thus we sensibly neglect them.
 
-\item \textbf{assumption 3} Demotion won't occur.
+\item \textbf{assumption 3} The hot water from the faucet has a constant flow velocity and temperature.
 
-\item \textbf{assumption 4} Administrative clerk won't promote or be
-  transferred.
+\item \textbf{assumption 4} There is no convection in the water.
 
-\item \textbf{assumption 5} For the promotion probability and
-  organization change, the other factors effects the churn probability
-  is invariable.
+Since the temperature of water in the bathtub is relatively uniform, the slight convection won't influence heat exchange.
 
-Though churn derives from varieties of reasons and they are actually
-lacking of known conditions and data to estimate them, we have to
-regard it as stable in our model.
-
-\item \textbf{assumption 6} Each division or office have at least one
-  middle manager or senior manager.
-
+\item \textbf{assumption 5} Water, bathtub, person and the surrounding air compose a closed heat system.
 \end{itemize}

### 2016-02-01 Tex/paper.tex
new

@@
 \usepackage{lastpage}
-\lhead{Team \# 33131}
+\lhead{Team \# 53768}
 \rhead{Page \thepage{} of \pageref{LastPage}}
@@
 
-Figure \ref{1_p} shows thermal analysis of water in bathtub.
+Figure \ref{1_p} shows thermal analysis of water in bathtub
+In the photo, $W_1$ is heat exchange between the person and water, while $W_2$ is heat from water vaporization.
+$W_3$ stands for heat exchange between the bathtub and water, and $W_4$ is heat conductivity between water and air.
+$W_5$ represents heat exchange between the bathtub and air, and $W_6$ is heat increasement with hot in-water.
+
 \begin{figure}[htb]
@@
 
-First, we assume that the heat change of all the water in a tiny time $\Delta t$ from $t_1$ to $t_2$ is $\Delta Q$.
+First, we assume that the heat change of all the water in a tiny time $\Delta t$ from $t_1$ to $t_2fv$ is $\Delta Q$.
 As shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.

### 2016-02-02 Tex/paper.tex
final correction added

@@
 
-\title{Human Capital Model} \date{\today{}}
+\title{Take A Relaxing Bath} \date{\today{}}
 \maketitle
@@
 \item Build a basic model that demonstrates the change of the temperature in the bathtub in space and time without other interventions.
-\item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the person or so.
+\item Figure out the influence of parameters such as the shape of the bathtub or the motions made by the bather or so.
 \item Propose a strategy to keep the temperature as even as possible.
@@
 In the first step, we build the simplest model.
-The shape of the bathtub is a cuboid, and the person will stay still.
-In the second step, the person moves slowly and the shape of the bathtub changes.
+The shape of the bathtub is a cuboid, and the bather will stay still.
+In the second step, the bather moves slowly and the shape of the bathtub changes.
 In the third step, we develop the conclusion of the strategy.
@@
   ${\gamma}_1$   &Heat exchange coefficient between water and air \\
-  ${\gamma}_2$   &Heat exchange coefficient between water and person \\
+  ${\gamma}_2$   &Heat exchange coefficient between water and bather \\
   ${\gamma}_3$   &Heat exchange coefficient between water and bathtub \\
@@
   $u_1$          &Temperature of air \\
-  $u_2$          &Temperature of person's surface \\
+  $u_2$          &Temperature of bather's surface \\
   $u_3$          &Temperature of bathtub \\
@@
 \begin{itemize}
-\item \textbf{assumption 1} The surface temperature of bathtub and the person keeps constant.
+\item \textbf{assumption 1} The surface temperature of bathtub and the bather keeps constant.
 
@@
 
-\item \textbf{assumption 5} Water, bathtub, person and the surrounding air compose a closed heat system.
+\item \textbf{assumption 5} Water, bathtub, bather and the surrounding air compose a closed heat system.
 \end{itemize}
@@
 % the main section of the paper
-\section{Water in the Bathtub Model}
+\section{PDE Model for Heating Water}
 \label{sec:human-capital-model}
@@
 In our model, five factors account for heat transfer of water: heat exchange between water and air, heat
-exchange between water and the person, heat exchange between water and the bathtub, heat energy of hot water from the
+exchange between water and the bather, heat exchange between water and the bathtub, heat energy of hot water from the
 faucet and heat energy of water flow outside. According to thermology, we deduce the equation
@@
 Figure \ref{1_p} shows thermal analysis of water in bathtub
-In the photo, $W_1$ is heat exchange between the person and water, while $W_2$ is heat from water vaporization.
+In the photo, $W_1$ is heat exchange between the bather and water, while $W_2$ is heat from water vaporization.
 $W_3$ stands for heat exchange between the bathtub and water, and $W_4$ is heat conductivity between water and air.
@@
 First, we assume that the heat change of all the water in a tiny time $\Delta t$ from $t_1$ to $t_2fv$ is $\Delta Q$.
-As shown in Figure 1, heat of water in the bathtub exchanges with air, the person and the bathtub.
+As shown in Figure 1, heat of water in the bathtub exchanges with air, the bather and the bathtub.
 In addition, heat changes when the hot water flows in and the excess water flows out.
@@
 \end{equation}
-in which $\Delta Q_1$ is the heat transferred from air, person and bathtub,
+in which $\Delta Q_1$ is the heat transferred from air, bather and bathtub,
 $\Delta Q_2$ is the heat of the hot water from the faucet in $\Delta t$,
@@
 
-The boundary of water consists of four parts: water-air boundary, water-person boundary, water-bathtub boundary, and the square for faucet. We denote them as
+The boundary of water consists of four parts: water-air boundary, water-bather boundary, water-bathtub boundary, and the square for faucet. We denote them as
 ${\Gamma}_1$, ${\Gamma}_2$, ${\Gamma}_3$, ${\Gamma}_4$ respectively.
@@
 \end{equation}
-In the equation, $u_2$ is the surface temperature of the person. We assume it is constant. $u_4$ is the temperature of hot water.
+In the equation, $u_2$ is the surface temperature of the bather. We assume it is constant. $u_4$ is the temperature of hot water.
 
@@
 
-$u_1$, the temperature of air, is time-dependant, because water vapor transfer heat to air.
+$u_1$, the temperature of air, is time-dependant because water vapor transfer heat to air.
 We can calculate $u_1$ by calculating the energy of water vapor evaporating in the air.
@@
 \label{sec:PDE solution}
-Since our equations are complex and the region is quite irregular, it's impossible to get a analytical solution. Finite element method is normally adopted to deal with this kind of problem.
+Since our equations are complex and the region is quite irregular, it's impossible to get an analytical solution. Finite element method is normally adopted to deal with this kind of problem.
 
@@
 and the initial value condition is $35\,^{\circ}\mathrm{C}$.
- We take 120s as time period. The following graphs show the results we get.
+ We set 120s as time period. The following graphs show the results we get.
 
@@
 
-\subsection{Parameters of Person}
-\label{sec:parameters of person}
+\subsection{Parameters of Bather}
+\label{sec:parameters of bather}
 \begin{itemize}
@@
 
-\section{Non-technical explanation}
+\section{Non-technical Explanation}
 
